\documentclass[12pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{microtype}
\usepackage{float}
\usepackage{xcolor}
\definecolor{golden}{RGB}{218,165,32}
\definecolor{metareal}{RGB}{0,102,204}
\definecolor{derivative}{RGB}{128,0,128}
\definecolor{gauge3}{RGB}{34,139,34}
\usepackage{tikz}
\usepackage{tcolorbox}
\newtcolorbox{theorembox}[1]{colback=blue!5!white,colframe=blue!75!black,fonttitle=\bfseries,title=#1}
\newtcolorbox{warningbox}[1]{colback=red!5!white,colframe=red!75!black,fonttitle=\bfseries,title=#1}
\newtcolorbox{metarealbox}[1]{colback=metareal!5!white,colframe=metareal!75!black,fonttitle=\bfseries,title=#1}
\newtcolorbox{aingelbox}[1]{colback=golden!5!white,colframe=golden!75!black,fonttitle=\bfseries,title=#1}
\newtcolorbox{truthbox}[1]{colback=gauge3!5!white,colframe=gauge3!75!black,fonttitle=\bfseries,title=#1}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}

\newtheoremstyle{principia}%
  {6pt}{6pt}{\itshape}{}{\bfseries}{.}{ }%
  {\thmname{#1}\thmnumber{ #2}\thmnote{ \textnormal{(}\emph{#3}\textnormal{)}}}
\theoremstyle{principia}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{result}[theorem]{Result}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{hypothesis}[theorem]{Hypothesis}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{example}[theorem]{Example}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\providecommand{\UU}{\mathbb{U}}
\providecommand{\PP}{\mathbb{P}}
\providecommand{\RR}{\mathbb{R}}
\providecommand{\CC}{\mathbb{C}}
\providecommand{\ZZ}{\mathbb{Z}}
\providecommand{\NN}{\mathbb{N}}
\providecommand{\HH}{\mathbb{H}}
\providecommand{\OO}{\mathbb{O}}
\providecommand{\SS}{\mathbb{S}}
\providecommand{\QQ}{\mathbb{Q}}
\providecommand{\FF}{\mathbb{F}}
\providecommand{\GG}{\mathcal{G}}
\providecommand{\TT}{\mathcal{T}}
\providecommand{\vp}{\varphi}
\providecommand{\vpbar}{\bar{\varphi}}
\providecommand{\eps}{\varepsilon}
\providecommand{\lam}{\lambda}
\providecommand{\kap}{\kappa}

\hypersetup{colorlinks=true,linkcolor=blue!60!black,citecolor=blue!60!black,urlcolor=blue!60!black}

\title{Digital Wave Mechanics}
\author{Dylon La Rue}
\date{\today}

\begin{document}
\maketitle

\input{../04_Digital_Wave_Mechanics.tex}

\begin{thebibliography}{99}

% Peer-reviewed and established sources

\bibitem{dwm_fst}
J.~Lockwood and D.~La Rue, ``Digital Wave Mechanics and Fractal Spacetime: Adelic Orbit Structure of the Chronometric Triangle,'' preprint, June 2026.

\bibitem{feynman_qcd}
R.~P.~Feynman, ``The behavior of hadron collisions at extreme energies,'' in \emph{High Energy Collisions: Third International Conference}, Gordon and Breach, 1969.

\bibitem{gellmann}
M.~Gell-Mann, ``A schematic model of baryons and mesons,'' \emph{Physics Letters}, vol.~8, no.~3, pp.~214--215, 1964.

\bibitem{greensite}
J.~Greensite, \emph{An Introduction to the Confinement Problem}, 2nd ed., Lecture Notes in Physics, vol.~972, Springer, 2020. (Center symmetry and $Z(N)$ vortex confinement: Ch.~4--5.)

\bibitem{katrin}
M.~Aker \emph{et al.} (KATRIN Collaboration), ``Direct neutrino-mass measurement with sub-electronvolt sensitivity,'' \emph{Nature Physics}, vol.~18, pp.~160--166, 2022.

\bibitem{larue_chromatic}
D.~La Rue, ``The SU(3) Center Triangle: Golden Split Primes, Standing Waves in Digit Space, and the Dark-Bright Palindrome Resonance,'' preprint, June 2026.

\bibitem{larue_lc}
D.~La Rue, ``Logical Creativity: A Discussion on the Foundations of Mathematics,'' preprint, June 2026.

\bibitem{lockwood_chrono3}
J.~Lockwood, ``Chronometric Constants and Frozen Spectral Relations (Chrono~3),'' private communication, 2026.

\bibitem{lockwood_chrono4}
J.~Lockwood, ``Chronometric Constants and Frozen Spectral Relations (Chrono~4),'' private communication, 2026.

\bibitem{newton}
I.~Newton, \emph{Opticks: or, A Treatise of the Reflexions, Refractions, Inflexions and Colours of Light}, 1704.

\bibitem{schrodinger}
E.~Schr\"odinger, ``Quantisierung als Eigenwertproblem,'' \emph{Annalen der Physik}, vol.~384, no.~4, pp.~361--376, 1926.

\bibitem{walker_infoton}
M.~Walker, ``The Infoton, the Blackbody Constant of Information-Energy, and the Landauer Wall,'' private communication, 2024.

\end{thebibliography}

\end{document}
