\documentclass[12pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{microtype}
\usepackage{float}
\usepackage{xcolor}
\definecolor{golden}{RGB}{218,165,32}
\definecolor{metareal}{RGB}{0,102,204}
\definecolor{derivative}{RGB}{128,0,128}
\definecolor{gauge3}{RGB}{34,139,34}
\usepackage{tikz}
\usepackage{tcolorbox}
\newtcolorbox{theorembox}[1]{colback=blue!5!white,colframe=blue!75!black,fonttitle=\bfseries,title=#1}
\newtcolorbox{warningbox}[1]{colback=red!5!white,colframe=red!75!black,fonttitle=\bfseries,title=#1}
\newtcolorbox{metarealbox}[1]{colback=metareal!5!white,colframe=metareal!75!black,fonttitle=\bfseries,title=#1}
\newtcolorbox{aingelbox}[1]{colback=golden!5!white,colframe=golden!75!black,fonttitle=\bfseries,title=#1}
\newtcolorbox{truthbox}[1]{colback=gauge3!5!white,colframe=gauge3!75!black,fonttitle=\bfseries,title=#1}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}

\newtheoremstyle{principia}%
  {6pt}{6pt}{\itshape}{}{\bfseries}{.}{ }%
  {\thmname{#1}\thmnumber{ #2}\thmnote{ \textnormal{(}\emph{#3}\textnormal{)}}}
\theoremstyle{principia}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{result}[theorem]{Result}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{hypothesis}[theorem]{Hypothesis}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{example}[theorem]{Example}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\providecommand{\UU}{\mathbb{U}}
\providecommand{\PP}{\mathbb{P}}
\providecommand{\RR}{\mathbb{R}}
\providecommand{\CC}{\mathbb{C}}
\providecommand{\ZZ}{\mathbb{Z}}
\providecommand{\NN}{\mathbb{N}}
\providecommand{\HH}{\mathbb{H}}
\providecommand{\OO}{\mathbb{O}}
\providecommand{\SS}{\mathbb{S}}
\providecommand{\QQ}{\mathbb{Q}}
\providecommand{\FF}{\mathbb{F}}
\providecommand{\GG}{\mathcal{G}}
\providecommand{\TT}{\mathcal{T}}
\providecommand{\vp}{\varphi}
\providecommand{\vpbar}{\bar{\varphi}}
\providecommand{\eps}{\varepsilon}
\providecommand{\lam}{\lambda}
\providecommand{\kap}{\kappa}

\hypersetup{colorlinks=true,linkcolor=blue!60!black,citecolor=blue!60!black,urlcolor=blue!60!black}

\title{Prime Field Mechanics and Negentropy}
\author{Dylon La Rue}
\date{\today}

\begin{document}
\maketitle

\input{../05_Prime_Field_Theory.tex}

\begin{thebibliography}{99}

% Peer-reviewed and established sources

\bibitem{aaronson2020}
S.~Aaronson,
``The Busy Beaver Frontier,''
\emph{ACM SIGACT News} 51(3), 32--54 (2020).

\bibitem{coppersmith1994}
D.~Coppersmith,
``An approximate Fourier transform,''
IBM Research Report RC19642 (1994).

\bibitem{dwm}
D.~La Rue,
``Digital Wave Mechanics,'' 2025.

\bibitem{dwm_fst}
J.~Lockwood and D.~La Rue, ``Digital Wave Mechanics and Fractal Spacetime: Adelic Orbit Structure of the Chronometric Triangle,'' preprint, June 2026.

\bibitem{goodstein1947}
R.~L.~Goodstein,
``Transfinite Ordinals in Recursive Number Theory,''
\emph{Journal of Symbolic Logic} 12(4), 123--129 (1947).

\bibitem{knuth1976}
D.~E.~Knuth,
``Mathematics and Computer Science: Coping with Finiteness,''
\emph{Science} 194(4271), 1235--1242 (1976).
Introduces the up-arrow notation for Goodstein's hyperoperation hierarchy.

\bibitem{krapivin2025optimal}
M.~Farach-Colton, A.~Krapivin, and W.~Kuszmaul,
``Optimal Bounds for Open Addressing Without Reordering,''
arXiv preprint arXiv:2501.02305 (2025).

\bibitem{larue_chromatic}
D.~La Rue, ``The SU(3) Center Triangle: Golden Split Primes, Standing Waves in Digit Space, and the Dark-Bright Palindrome Resonance,'' preprint, June 2026.

\bibitem{larue_lc}
D.~La Rue, ``Logical Creativity: A Discussion on the Foundations of Mathematics,'' preprint, June 2026.

\bibitem{lockwood_chrono}
J.~Lockwood,
``Chronometric Constants and Frozen Spectral Relations,''
Private communication, 2026.

\bibitem{lockwood_larue_dwm}
J.~Lockwood and D.~La Rue,
``Digital Wave Mechanics: From Newton's Prism to Standing Waves
in Finite Golden Fields,'' 2026.

\bibitem{lockwood_zpe2025}
J.~Lockwood,
``Fractal Spacetime and Zero-Point Energy,'' 2025.

\bibitem{pollard1971}
J.~M.~Pollard,
``The fast Fourier transform in a finite field,''
\emph{Math.\ Comp.} 25(114), 365--374 (1971).

\bibitem{rado1962}
T.~Rad\'o,
``On Non-Computable Functions,''
\emph{Bell System Technical Journal} 41(3), 877--884 (1962).

\bibitem{schrodinger44}
E.~Schr\"odinger,
\emph{What is Life? The Physical Aspect of the Living Cell},
Cambridge University Press, 1944.
Chapter~6: ``Order, Disorder, and Entropy.''

\bibitem{shannon48}
C.~E.~Shannon,
``A Mathematical Theory of Communication,''
\emph{Bell System Technical Journal} 27, 379--423, 623--656 (1948).

\bibitem{shor1994}
P.~W.~Shor,
``Algorithms for quantum computation: discrete logarithms and factoring,''
\emph{Proceedings 35th Annual Symposium on Foundations of Computer Science}, IEEE, 124--134 (1994).

\end{thebibliography}

\end{document}
