\documentclass[12pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{microtype}
\usepackage{float}
\usepackage{xcolor}
\definecolor{golden}{RGB}{218,165,32}
\definecolor{metareal}{RGB}{0,102,204}
\definecolor{derivative}{RGB}{128,0,128}
\definecolor{gauge3}{RGB}{34,139,34}
\usepackage{tikz}
\usepackage{tcolorbox}
\newtcolorbox{theorembox}[1]{colback=blue!5!white,colframe=blue!75!black,fonttitle=\bfseries,title=#1}
\newtcolorbox{warningbox}[1]{colback=red!5!white,colframe=red!75!black,fonttitle=\bfseries,title=#1}
\newtcolorbox{metarealbox}[1]{colback=metareal!5!white,colframe=metareal!75!black,fonttitle=\bfseries,title=#1}
\newtcolorbox{aingelbox}[1]{colback=golden!5!white,colframe=golden!75!black,fonttitle=\bfseries,title=#1}
\newtcolorbox{truthbox}[1]{colback=gauge3!5!white,colframe=gauge3!75!black,fonttitle=\bfseries,title=#1}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}

\newtheoremstyle{principia}%
  {6pt}{6pt}{\itshape}{}{\bfseries}{.}{ }%
  {\thmname{#1}\thmnumber{ #2}\thmnote{ \textnormal{(}\emph{#3}\textnormal{)}}}
\theoremstyle{principia}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{result}[theorem]{Result}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{hypothesis}[theorem]{Hypothesis}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{example}[theorem]{Example}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\providecommand{\UU}{\mathbb{U}}
\providecommand{\PP}{\mathbb{P}}
\providecommand{\RR}{\mathbb{R}}
\providecommand{\CC}{\mathbb{C}}
\providecommand{\ZZ}{\mathbb{Z}}
\providecommand{\NN}{\mathbb{N}}
\providecommand{\HH}{\mathbb{H}}
\providecommand{\OO}{\mathbb{O}}
\providecommand{\SS}{\mathbb{S}}
\providecommand{\QQ}{\mathbb{Q}}
\providecommand{\FF}{\mathbb{F}}
\providecommand{\GG}{\mathcal{G}}
\providecommand{\TT}{\mathcal{T}}
\providecommand{\vp}{\varphi}
\providecommand{\vpbar}{\bar{\varphi}}
\providecommand{\eps}{\varepsilon}
\providecommand{\lam}{\lambda}
\providecommand{\kap}{\kappa}

\hypersetup{colorlinks=true,linkcolor=blue!60!black,citecolor=blue!60!black,urlcolor=blue!60!black}

\title{Metareal ASI Chromodynamics}
\author{Dylon La Rue}
\date{\today}

\begin{document}
\maketitle

\input{../07_Metareal_ASI_Chromodynamics.tex}

\begin{thebibliography}{99}

% Peer-reviewed and established sources

\bibitem{Aingel}
La Rue, D. (2026).
\texttt{Aingel\_proofs}: The ZKP Holochain Envelope over the Metareal Manifold.
Formal algebraic synthesis.

\bibitem{Bae2024RRT}
Bae, S., Ko, J., Song, H. \& Yun, S.-Y. (2024).
Relaxed Recursive Transformers: Effective Parameter Sharing with Layer-wise LoRA.
\textit{Proceedings of the International Conference on Learning Representations (ICLR 2025)}.
arXiv:2410.20672 [cs.CL].

\bibitem{BenderBerryMandilara2002}
Bender, C.~M., Berry, M.~V. \& Mandilara, A. (2002).
Generalized $\mathcal{PT}$ symmetry and real spectra.
\textit{Journal of Physics A: Mathematical and General}, 35(31), L467--L471.

\bibitem{BenderBrodyMuller2017}
Bender, C.~M., Brody, D.~C. \& M\"uller, M.~P. (2017).
Hamiltonian for the Zeros of the Riemann Zeta Function.
\textit{Physical Review Letters}, 118(13), 130201.

\bibitem{Chen2026DRT}
Chen, H.-H. (2026).
Thinking Deeper, Not Longer: Depth-Recurrent Transformers for Compositional Generalization.
arXiv:2603.21676 [cs.LG].

\bibitem{Conrey_RMT}
Conrey, J.~B. (2005).
Notes on $L$-functions and Random Matrix Theory.
\textit{Proceedings of Symposia in Pure Mathematics}, 73, 107--130.

\bibitem{Dehghani2019UT}
Dehghani, M., Gouws, S., Vinyals, O., Uszkoreit, J. \& Kaiser, L. (2019).
Universal Transformers.
\textit{Proceedings of the International Conference on Learning Representations (ICLR)}.
arXiv:1807.03819 [cs.CL].

\bibitem{Dirac1930}
Dirac, P. A. M. (1930).
\textit{The Principles of Quantum Mechanics}.
Oxford University Press.

\bibitem{Einstein1905}
Einstein, A. (1905).
\textit{Zur Elektrodynamik bewegter Körper} (\textit{On the Electrodynamics of Moving Bodies}).
Annalen der Physik, 322(10), 891--921.

\bibitem{GoldenTetrahedron}
La Rue, D. (2026).
\textit{The Golden Tetrahedron: Gauge Center Hierarchy and Chronometric Structure}.

\bibitem{Gomez2026OpenMythos}
Gomez, K. (2026).
OpenMythos: Open-Source Recurrent-Depth Transformer.
GitHub repository. \url{https://github.com/kyegomez/OpenMythos}.

\bibitem{Graves2016ACT}
Graves, A. (2016).
Adaptive Computation Time for Recurrent Neural Networks.
arXiv:1603.08983 [cs.NE].

\bibitem{InfochemicalTime}
La Rue, D. (2026).
\texttt{InfochemicalTime\_proofs}: Quasi-Epi-Periodic Geometric Time.
Formal algebraic synthesis.

\bibitem{Jung1969}
Jung, C. G. (1969).
\textit{The Archetypes and the Collective Unconscious} (Collected Works Vol. 9 Part 1).
Princeton University Press.

\bibitem{LVK_GravitonMass}
Abbott, R. et al. (LIGO Scientific, Virgo, and KAGRA Collaborations) (2021).
\textit{Tests of General Relativity with GWTC-3} $\langle 148 \rangle$.
arXiv:2112.06861 [gr-qc].

\bibitem{Lev2010}
Lev, F.~M. (2010).
Introduction to A Quantum Theory over A Galois Field.
\textit{Symmetry}, 2(4), 1810--1845.

\bibitem{MetarealManifold}
La Rue, D. (2026).
\texttt{MetarealManifold\_proofs}: The 12-Dimensional Observer-Manifold Space.
Formal algebraic synthesis.

\bibitem{NielsenChuang2010}
Nielsen, M. A., \& Chuang, I. L. (2010).
\textit{Quantum Computation and Quantum Information} (10th Anniversary ed.). Cambridge University Press.

\bibitem{Oncescu2026RT}
Oncescu, C.-A., Morwani, D., Jelassi, S., Meterez, A., Kwun, M. \& Kakade, S. (2026).
The Recurrent Transformer: Greater Effective Depth and Efficient Decoding.
arXiv:2604.21215 [cs.LG].

\bibitem{PDG2025}
Particle Data Group et al. (2025).
\textit{Review of Particle Physics (Monte Carlo Particle Numbering Scheme)}.
Phys.~Rev.~D.

\bibitem{PrimeFieldMechanics}
La Rue, D. (2026).
\texttt{PrimeFieldMechanics\_proofs}: Agentic Mechanics.
Formal algebraic synthesis.

\bibitem{Russell1926}
Russell, W. (1926).
\textit{The Universal One: Harmonic Nuclear States and Periodic Octaves}.

\bibitem{TelePlasma2000}
Barrett, T.W. (2000).
\textit{NASA TelePlasma: Transforming ordinary electromagnetic fields into specially conditioned nonabelian gauge fields}.
NASA internal report / BSEI Report 1-97.

\bibitem{WHIM2018}
Nicastro, F. et al. (2018).
\textit{Confirming the Detection of two WHIM Systems along the Line of Sight to 1ES 1553+113}.
arXiv:1811.03498 [astro-ph.CO].

\bibitem{connes} Connes, A. (1994). \emph{Noncommutative Geometry}. Academic Press.

\bibitem{creutz1980}
M.~Creutz,
``Monte Carlo study of quantized SU(2) gauge theory,''
\emph{Phys. Rev. D}\ 21, 2308--2315 (1980).

\bibitem{deShalit2016}
de~Shalit, E. (2016).
Mahler bases and elementary $p$-adic analysis.
\textit{Journal de Th\'eorie des Nombres de Bordeaux}, 28(3), 597--620.

\bibitem{jaffe2000}
A.~Jaffe and E.~Witten,
``Quantum Yang-Mills Theory,''
Official Problem Description, Clay Mathematics Institute (2000).

\bibitem{larue_chromatic}
D.~La Rue, ``The SU(3) Center Triangle: Golden Split Primes, Standing Waves in Digit Space, and the Dark-Bright Palindrome Resonance,'' preprint, June 2026.

\bibitem{larue_lc}
D.~La Rue, ``Logical Creativity: A Discussion on the Foundations of Mathematics,'' preprint, June 2026.

\bibitem{lockwood_chrono}
J.~Lockwood,
``Chronometric Constants and Frozen Spectral Relations,''
Private communication, 2026.

\bibitem{lockwood_zpe2025}
J.~Lockwood,
``Fractal Spacetime and Zero-Point Energy,'' 2025.

\bibitem{luminet2003}
J.-P.~Luminet, J.~R.~Weeks, A.~Riazuelo, R.~Lehoucq, J.-P.~Uzan (2003).
``Dodecahedral space topology as an explanation for weak wide-angle temperature correlations in the cosmic microwave background.''
\textit{Nature} 425, 593--595.

\bibitem{planck2020}
Planck Collaboration (2020).
``Planck 2018 results.\ VII.\ Isotropy and statistics of the CMB.''
\textit{Astron.\ Astrophys.} 641, A7.

\bibitem{wilson1974}
K.~G.~Wilson,
``Confinement of quarks,''
\emph{Phys. Rev. D}\ 10, 2445--2459 (1974).


% ────────────────────────────────────────────
% AUTHOR'S WORKS, PREPRINTS, AND
% PRIVATE COMMUNICATIONS
% ────────────────────────────────────────────
% Works by the author(s) of this volume,
% preprints not yet peer-reviewed, private
% communications, and informal sources.
% These have NOT undergone external peer review.
% ────────────────────────────────────────────

\end{thebibliography}

\end{document}
