\documentclass[12pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{microtype}
\usepackage{float}
\usepackage{xcolor}
\definecolor{golden}{RGB}{218,165,32}
\definecolor{metareal}{RGB}{0,102,204}
\definecolor{derivative}{RGB}{128,0,128}
\definecolor{gauge3}{RGB}{34,139,34}
\usepackage{tikz}
\usepackage{tcolorbox}
\newtcolorbox{theorembox}[1]{colback=blue!5!white,colframe=blue!75!black,fonttitle=\bfseries,title=#1}
\newtcolorbox{warningbox}[1]{colback=red!5!white,colframe=red!75!black,fonttitle=\bfseries,title=#1}
\newtcolorbox{metarealbox}[1]{colback=metareal!5!white,colframe=metareal!75!black,fonttitle=\bfseries,title=#1}
\newtcolorbox{aingelbox}[1]{colback=golden!5!white,colframe=golden!75!black,fonttitle=\bfseries,title=#1}
\newtcolorbox{truthbox}[1]{colback=gauge3!5!white,colframe=gauge3!75!black,fonttitle=\bfseries,title=#1}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}

\newtheoremstyle{principia}%
  {6pt}{6pt}{\itshape}{}{\bfseries}{.}{ }%
  {\thmname{#1}\thmnumber{ #2}\thmnote{ \textnormal{(}\emph{#3}\textnormal{)}}}
\theoremstyle{principia}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{result}[theorem]{Result}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{hypothesis}[theorem]{Hypothesis}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{example}[theorem]{Example}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\providecommand{\UU}{\mathbb{U}}
\providecommand{\PP}{\mathbb{P}}
\providecommand{\RR}{\mathbb{R}}
\providecommand{\CC}{\mathbb{C}}
\providecommand{\ZZ}{\mathbb{Z}}
\providecommand{\NN}{\mathbb{N}}
\providecommand{\HH}{\mathbb{H}}
\providecommand{\OO}{\mathbb{O}}
\providecommand{\SS}{\mathbb{S}}
\providecommand{\QQ}{\mathbb{Q}}
\providecommand{\FF}{\mathbb{F}}
\providecommand{\GG}{\mathcal{G}}
\providecommand{\TT}{\mathcal{T}}
\providecommand{\vp}{\varphi}
\providecommand{\vpbar}{\bar{\varphi}}
\providecommand{\eps}{\varepsilon}
\providecommand{\lam}{\lambda}
\providecommand{\kap}{\kappa}

\hypersetup{colorlinks=true,linkcolor=blue!60!black,citecolor=blue!60!black,urlcolor=blue!60!black}

\title{Multimodal Metamaterial Mechanisms}
\author{Dylon La Rue}
\date{\today}

\begin{document}
\maketitle

\input{../09_Multimodal_Mechanisms.tex}

\begin{thebibliography}{99}

% Peer-reviewed and established sources

\bibitem{Russell1926}
Russell, W. (1926).
\textit{The Universal One: Harmonic Nuclear States and Periodic Octaves}.

\bibitem{atasoy2017} S.~Atasoy et al., ``Connectome-harmonic decomposition of human brain activity reveals dynamical repertoire re-organization under LSD,'' \emph{Scientific Reports}\ 7, 17661 (2017).

\bibitem{bender-berry-mandilara-12} C.~M.~Bender, M.~V.~Berry, and A.~Mandilara, ``Generalized $\mathcal{PT}$ symmetry and real spectra,'' \emph{J.\ Phys.\ A}\ 35(31), L467--L471 (2002).

\bibitem{carhart2019} R.~L.~Carhart-Harris and K.~J.~Friston, ``REBUS and the Anarchic Brain: Toward a Unified Model of the Brain Action of Psychedelics,'' \emph{Pharmacol Rev}\ 71(3), 316-344 (2019).

\bibitem{conrey-rmt-12} J.~B.~Conrey, ``Notes on $L$-functions and Random Matrix Theory,'' \emph{Proc.\ Sympos.\ Pure Math.}\ 73, 107--130 (2005).

\bibitem{deshalit-mahler-12} E.~de~Shalit, ``Mahler bases and elementary $p$-adic analysis,'' \emph{J.\ Th\'eorie des Nombres de Bordeaux}\ 28(3), 597--620 (2016).

\bibitem{dwm}
D.~La Rue,
``Digital Wave Mechanics,'' 2025.

\bibitem{dwm_fst}
J.~Lockwood and D.~La Rue, ``Digital Wave Mechanics and Fractal Spacetime: Adelic Orbit Structure of the Chronometric Triangle,'' preprint, June 2026.

\bibitem{fernstrom71} J.~D.~Fernstrom and R.~J.~Wurtman, ``Brain serotonin content: physiological regulation by plasma neutral amino acids,'' \emph{Science}\ 173, 149 (1971).

\bibitem{fractalEEG} S.~Buzs\'aki and K.~Mizuseki, ``The log-dynamic brain: how skewed distributions affect network operations,'' \emph{Nature Reviews Neuroscience}\ 15, 264-278 (2014).

\bibitem{fractalPathology} E.~Bullmore et al., ``Fractal analysis of the electroencephalogram in depression and schizophrenia,'' \emph{IEEE Trans Biomed Eng}\ (1994).

\bibitem{hameroff2014} S.~Hameroff and R.~Penrose, ``Consciousness in the universe: A review of the `Orch OR' theory,'' \emph{Physics of Life Reviews}\ 11(1), 39--78 (2014).

\bibitem{konkoly2021} K.~R.~Konkoly et al., ``Real-time dialogue between experimenters and dreamers during REM sleep,'' \emph{Current Biology}\ 31(7), 1417-1427.e6 (2021).

\bibitem{lc} D.~La Rue, \emph{Logical Creativity}, Protoreal Zeta Series, 2026.

\bibitem{mckinney05} J.~McKinney et al., ``A revised mechanism for tryptophan hydroxylase,'' \emph{J.~Biol.~Chem.}\ 280, 13265 (2005).

\bibitem{mrs_glutamate} R.~A.~E.~Edden et al., ``Proton MR spectroscopy of GABA, glutamate, and glutamine,'' \emph{Neuroimage}, 2012.

\bibitem{mrs_variance} A.~Bogaschewsky et al., ``Reproducibility of Glx and GABA measurements in the human brain,'' \emph{Magnetic Resonance in Medicine}, 2019.

\bibitem{nagatsu64} T.~Nagatsu, M.~Levitt, and S.~Udenfriend, ``Tyrosine Hydroxylase: The Initial Step in Norepinephrine Biosynthesis,'' \emph{J Biol Chem}\ 239, 2910--2917 (1964).

\bibitem{padicCognition} A.~Khrennikov, \emph{Information Dynamics in Cognitive, Psychological, Social and Anomalous Phenomena}, Springer (2004).

\bibitem{pitkanenTGD} M.~Pitk\"anen, ``TGD Inspired Theory of Consciousness,'' \emph{Journal of Non-Locality and Remote Mental Interactions}\ 1 (2002).

\bibitem{rj2} J.~Lockwood and D.~Hansley, \emph{Royal Jelly: Field--Transport Foundations for Bioelectromagnetics}, Spectrality Institute, 2025.

\bibitem{rja} D.~La Rue, \emph{Transport--Algebraic Correspondence in Bioelectromagnetics: An Analysis of the Royal Jelly Framework}, InfoPhys Axioms, 2026.

\bibitem{savitz20} J.~Savitz, ``The kynurenine pathway: a finger in every pie,'' \emph{Mol Psychiatry}\ 25, 131--147 (2020).

\bibitem{schwieler16} L.~Schwieler et al., ``Electroconvulsive therapy suppresses the neurotoxic branch of the kynurenine pathway in treatment-resistant depressed patients,'' \emph{Transl Psychiatry}\ 6, e906 (2016).

\bibitem{sono96} M.~Sono et al., ``Heme-containing oxygenases,'' \emph{Chem.\ Rev.}\ 96, 2841 (1996).

\bibitem{srinivasan15} B.~Srinivasan et al., ``TEER measurement techniques for in vitro barrier model systems,'' \emph{JALA}\ 20, 107 (2015).

\bibitem{stockigt11} J.~St\"ockigt et al., ``The Pictet--Spengler reaction in nature and in organic chemistry,'' \emph{Angew.~Chem.}\ 50, 7580 (2011).

\end{thebibliography}

\end{document}
