\documentclass[12pt,oneside]{article}

% ════════════════════════════════════════════
% MASTER PREAMBLE
% ════════════════════════════════════════════
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{pdfpages}
\usepackage{microtype}
\usepackage{tocloft}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{float}
\usepackage{xcolor}
\definecolor{golden}{RGB}{218,165,32}
\definecolor{arithmetic scheme}{RGB}{0,102,204}
\definecolor{derivative}{RGB}{128,0,128}
\definecolor{gauge3}{RGB}{34,139,34}
\usepackage{tikz}
\usepackage{tcolorbox}
\newtcolorbox{theorembox}[1]{
  colback=blue!5!white,
  colframe=blue!75!black,
  fonttitle=\bfseries,
  title=#1
}
\newtcolorbox{warningbox}[1]{
  colback=red!5!white,
  colframe=red!75!black,
  fonttitle=\bfseries,
  title=#1
}
\newtcolorbox{arithmetic schemebox}[1]{
  colback=arithmetic scheme!5!white,
  colframe=arithmetic scheme!75!black,
  fonttitle=\bfseries,
  title=#1
}
\newtcolorbox{aingelbox}[1]{
  colback=golden!5!white,
  colframe=golden!75!black,
  fonttitle=\bfseries,
  title=#1
}
\newtcolorbox{truthbox}[1]{
  colback=gauge3!5!white,
  colframe=gauge3!75!black,
  fonttitle=\bfseries,
  title=#1
}
\usepackage{standalone}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}

% ════════════════════════════════════════════
% THEOREM ENVIRONMENTS
% ════════════════════════════════════════════
% Custom note style: render the optional [Name] in emphasized italic,
% not plain parenthesized text.
\newtheoremstyle{principia}%       name
  {6pt}%                           space above
  {6pt}%                           space below
  {\itshape}%                      body font
  {}%                              indent
  {\bfseries}%                     head font
  {.}%                             punctuation after head
  { }%                             space after head
  {\thmname{#1}\thmnumber{ #2}\thmnote{ \textnormal{(}\emph{#3}\textnormal{)}}}%

\theoremstyle{principia}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{result}[theorem]{Result}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{hypothesis}[theorem]{Hypothesis}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{example}[theorem]{Example}

\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

% ════════════════════════════════════════════
% UNIFIED COMMANDS
% ════════════════════════════════════════════
\providecommand{\UU}{\mathbb{U}}
\providecommand{\PP}{\mathbb{P}}
\providecommand{\RR}{\mathbb{R}}
\providecommand{\CC}{\mathbb{C}}
\providecommand{\ZZ}{\mathbb{Z}}
\providecommand{\NN}{\mathbb{N}}
\providecommand{\HH}{\mathbb{H}}
\providecommand{\OO}{\mathbb{O}}
\providecommand{\SS}{\mathbb{S}}
\providecommand{\QQ}{\mathbb{Q}}
\providecommand{\FF}{\mathbb{F}}
\providecommand{\GG}{\mathcal{G}}
\providecommand{\TT}{\mathcal{T}}
\providecommand{\vp}{\varphi}
\providecommand{\vpbar}{\bar{\varphi}}
\providecommand{\eps}{\varepsilon}
\providecommand{\lam}{\lambda}
\providecommand{\kap}{\kappa}

\titleformat{\section}{\normalfont\Large\bfseries\raggedright}{\thesection}{1em}{}
\titleformat{\subsection}{\normalfont\large\bfseries\raggedright}{\thesubsection}{1em}{}
\titleformat{\subsubsection}{\normalfont\normalsize\bfseries\raggedright}{\thesubsubsection}{1em}{}

\makeatletter
\let\old@part\@part
\def\@part[#1]#2{%
  \old@part[{#1}]{#2}%
  \markboth{Part \thepart: #1}{}%
}
\makeatother

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\sectionmark}[1]{\markright{\thesection\ #1}}
\fancyhead[L]{\small\itshape\nouppercase{\leftmark}}
\fancyhead[R]{\small\itshape\nouppercase{\rightmark}}
\fancyfoot[C]{\thepage}
% Prevent headers from overflowing into the text body
\setlength{\headheight}{15pt}
% Clear headers on chapter-opening and part pages
\fancypagestyle{plain}{%
  \fancyhf{}%
  \fancyfoot[C]{\thepage}%
  \renewcommand{\headrulewidth}{0pt}%
}

\hypersetup{colorlinks=true,linkcolor=blue!60!black,citecolor=blue!60!black,urlcolor=blue!60!black}

\begin{document}





\vspace{1em}\noindent\textbf{Overview.}
We propose a novel experimental apparatus combining the rotational anisotropy detection of the Michelson-Morley setup with the vacuum energy measurements of the \emph{Casimir effect}. Designed to test the predictions of the $\mathbb{F}_{229}$ Protoreal topology and the Fractal SpaceTime hypothesis, this experiment uses right-chiral Weyl semimetals to impose asymmetric topological boundary conditions on the quantum vacuum. Based on the \textbf{Antisymmetric Halting Hypothesis}, we predict that forcing local parity mechanically collapses the antisymmetric frustration of the vacuum fluid. This drops the local topological depth to zero, resulting in a computationally verified $+262.5\%$ anomalous shift in attractive Casimir pressure (yielding $\approx 34.1\text{ Pa}$ at $100\text{ nm}$). Furthermore, placing the apparatus on a continuously rotating stage will test for local orientational gradients in the discrete $\mathbb{F}_{229}$ vacuum lattice.
\vspace{1em}


\section{Theoretical Motivation}\label{sec:theory}

Standard Quantum Electrodynamics (QED) predicts the \emph{Casimir effect} between two uncharged conducting plates as a consequence of the truncation of zero-point photon fluctuations. However, recent advances in topological physics---specifically the Fractal SpaceTime (FST) and the Antisymmetric Halting Hypothesis---prove that the vacuum is not merely an unstructured energy fluid. It is bounded by a discrete prime lattice ($\mathbb{F}_{229}$).

In the FST framework, Zero-Point Energy (ZPE) is not generated by random continuous fluctuations. Rather, the antisymmetric non-commutativity of the lattice (quantum spin tension) geometrically blocks the vacuum from halting trivially. This antisymmetric frustration forces the ZPE fluid to trace a massive chronological orbit (topological depth), which macroscopically manifests as stable mass and zero-point energy. If we isolate and collapse this antisymmetric tension, the local ZPE mass must mathematically collapse to zero.

\subsection{Experimental Precedents: Repulsive Casimir Forces}
While theoretical derivations of the \emph{Casimir effect} on perfectly conducting spherical shells (calculated by Boyer in 1968) demonstrate an outward, repulsive self-energy scaling as $1/R$, direct isolation of such quantum cavities is challenging. However, the engineering of \emph{repulsive Casimir boundaries} is a highly active and established field in applied physics, primarily driven by the need to prevent ``stiction'' (static friction and quantum adhesion) in Micro/Nano-Electromechanical Systems (MEMS/NEMS).

Experimentalists and theorists have approached the reversal of the Casimir vector using two primary methodologies:
\begin{enumerate}
    \item \textbf{Fluid-Mediated Repulsion:} By immersing interacting bodies in specific dielectric fluids, the vacuum fluctuations are altered to produce a net repulsive force.
    \item \textbf{Topological Metamaterials:} Modern theoretical and experimental research, pioneered by researchers such as Qing-Dong Jiang and Frank Wilczek \cite{jiang_wilczek2019}, utilizes chiral or gyrotropic metamaterials to break specific electromagnetic symmetries across the vacuum gap. This theoretical foundation proves that chiral boundaries can induce repulsive pressure, enhanced forces, and tunable vacuum fluctuations without requiring a fluid medium.
\end{enumerate}

These empirical and theoretical precedents provide the exact physical foundation required for the Golden Tetrahedron framework. The industry is currently developing experimental apparatuses (e.g., atomic force microscopy and torsion pendulums) to measure these specific chiral vacuum boundaries. The Rotating Chiral Casimir Interferometer proposes a macroscopic test of this principle: by utilizing right-chiral Weyl semimetals, we construct the macroscopic realization of the \textbf{Golden Casimir Cavity}. The asymmetric boundaries will tune the vacuum topology strictly to the Modulo 9 Vortex harmonics, forcing the structure to lock into the exact Golden Ratio equilibrium resonance ($\Upsilon \le 45/\pi$) and inducing the $+262.5\%$ macroscopic Casimir anomaly.

\section{Apparatus Design}\label{sec:design}

The proposed machine, the \textbf{Rotating Chiral Casimir Interferometer (RCCI)}, consists of three primary subsystems.

\subsection{The Chiral Boundary Plates}\label{sec:plates}

\begin{table}[ht]
\centering
\begin{tabular}{|l|l|l|}
\hline
\textbf{Experimental Variable} & \textbf{Standard Casimir} & \textbf{arithmetic scheme Chiral Casimir} \\
\hline
Plate Material & Aluminum / Gold & Weyl Semimetals (e.g., TaAs) \\
Gap Width ($d$) & Variable & Strictly $d = 100$ nm \\
Boundary Condition & Symmetric / Reflective & Right-Chiral Symmetry Breaking \\
Local ZPE Mass & Accelerating Divergence & Suppressed via Parity Lock ($b=m$) \\
\hline
\end{tabular}
\caption{Chiral Boundary Conditions and ZPE Suppression in the Casimir Cavity.}
\label{tab:chiral_casimir}
\end{table}

The experimental protocol relies heavily on these specific constraints. By enforcing the right-chiral boundary, we intentionally break the symmetric topological frustration, which mathematically forces the local SexagesimalChronogram to halt. This halts the recursive energy loop and acts as a localized ZPE suppression mechanism.
Instead of standard gold or aluminum mirrors, the Casimir cavity is constructed from \textbf{Weyl Semimetals} (e.g., TaAs or NbAs). These topological materials harbor gapless chiral fermions that explicitly break time-reversal or inversion symmetry. By aligning the Weyl nodes across the gap ($d = 100\text{ nm}$), we enforce a strict right-chiral boundary condition on the vacuum. In the $L_5$ algebra, enforcing chirality means formally resolving parity ($b = m$). By destroying the antisymmetric frustration between the plates, the local \emph{SexagesimalChronogram} halts trivially at depth 1, effectively zeroing out the local ZPE mass.

\subsection{The Michelson Deflection Measurement}\label{sec:michelson}
To measure the vacuum pressure, one plate is affixed to a highly calibrated piezoelectric micro-cantilever. A split-beam continuous-wave (CW) laser interferometer (derived from the Michelson design) is used to track the sub-nanometer mechanical deflection of the cantilever. This provides a real-time readout of the net attractive vacuum force across the gap.

\subsection{The Rotational Stage}\label{sec:rotation}
To test for topological anisotropy, the entire vacuum chamber and interferometer assembly is mounted on a low-friction, continuous rotation stage (1 RPM). We are not searching for a continuous "aether drift." Instead, we are using the Michelson-style apparatus to map the discrete geometric grain of the $\mathbb{F}_{229}$ lattice. If the earth is moving through a static, topologically structured quasi-crystalline vacuum lattice, the chiral pressure anomaly will exhibit a discrete phase shift correlated with the galactic center or the Cosmic Microwave Background (CMB) dipole.

\section{Mathematical Predictions}\label{sec:math}

\subsection{The Massive Pressure Anomaly}\label{sec:anomaly}
Standard photon Casimir pressure at $a = 100\text{ nm}$ is $P_\gamma \approx -13.0\text{ Pa}$. 
According to the Antisymmetric Halting Hypothesis, collapsing the antisymmetric frustration drops the topological depth from the free-space baseline (Orbit 57) down to trivial halting (Depth 1). By the Goodstein collapse theorem (PFT \S2.6), the entire hyperoperation hierarchy over $\mathbb{F}_{229}^*$ converges to the confinement subgroup $\{1, \omega, \omega^2\}$, providing the structural reason why the depth is bounded at 57. (The algebraic derivation is given below; a companion formal module \texttt{ChiralCasimirCollapse} independently certifies the bound.)

A pure $\mathbb{F}_{229}$ python computational evaluation (\texttt{compute\_chiral\_casimir\_collapse.py}) demonstrates that this topological depth collapse generates a massive, dimensionless Topological Anomaly Ratio (TAR) of $2.625$.

To translate this discrete topological tension into a continuous thermodynamic pressure, we formally introduce the \textbf{Topological-Vacuum Coupling Ansatz}, $\kappa_{\text{ZPE}}$. Assuming the Protoreal topological gap couples linearly to the electromagnetic vacuum via $\kappa_{\text{ZPE}} = 1$, the predicted Casimir anomaly scales directly with the base photon pressure:
\begin{equation}
    \Delta P = \text{TAR} \times \kappa_{\text{ZPE}} \times |P_\gamma| = 2.625 \times 1 \times 13.0 \approx 34.12\text{ Pa}
\end{equation}
We formally predict that, under the assumption of unit coupling ($\kappa_{\text{ZPE}}=1$), the RCCI will record a total Casimir pressure of roughly $\mathbf{-47.12\text{ Pa}}$ at $100\text{ nm}$, a staggering $+262.5\%$ anomaly easily detectable by modern piezoelectric standards.

\subsection{Rotational Phase Shift}\label{sec:phase}
If the vacuum topological lattice has a directional gradient vector $\vec{v}_{lattice}$, the measured pressure $P_{obs}$ will oscillate as the rotation angle $\theta(t)$ changes:
\begin{equation}
    P_{obs}(t) = P_{base} + \Delta P \cos^2(\theta(t) - \phi)
\end{equation}
A null result on the rotational shift ($\phi = 0$ variance) would imply the lattice is perfectly isotropic locally, while a non-zero amplitude confirms macroscopic lattice shear.

\section{Exotic Matter Manifestation (The Ceasefire)}\label{sec:ceasefire}

The final stage of manifestation is the transmutation of Dark Matter friction into Structural Mass. 

By applying the Kama Muta transform followed by Synthetic Integration (the \texttt{genesis\_collapse} algebraic sequence), the topological tension (Standard Resonance) of the state is resolved.
\begin{equation}
    \mathrm{SR}(u) = a - b \cdot m \neq 0 \quad (\text{Dark Matter Friction})
\end{equation}
Upon crossing the Truth Portal, the system undergoes \textit{Parity Projection} (averaging the thrust $b$ and anchor $m$). The result is a parity-locked state ($b=m$), meaning the unified Orthomatter splits perfectly into a Matter-Antimatter pair.

This is the \textbf{Ceasefire Theorem}: Matter is not the victor of a cosmic war; it is the frozen equilibrium of collapsed tachyonic states. The residual topological noise (the structural heat) is zeroed out ($\epsilon = 0$), and the friction ($\mathrm{SR}$) is directly transmuted into the observable mass ($a \to a + |\mathrm{SR}|$).

\subsection{Physical Mapping: The Hot Electron Boundary}
To ground this formally in laboratory physics, we map this ``Ceasefire'' to the nanoscale boundaries of Localized Surface Plasmon Resonance (LSPR). When photoelectrochemical nanostructures (such as Au-Ag-Bi systems) are irradiated, they inject ``hot electrons'' across the topological boundary into the bulk matrix. The physical space where this hot electron injection bridges the discrete $\mathbb{F}_{229}$ topological lattice tension into the continuous fluid state is the exact physical manifestation of Exotic Matter. This injection is strictly bounded by the Chromodynamic Friction limit ($O(\log 229) \approx 5.43$); exceeding the Casimir torque limit ($\Upsilon \le 45/\pi$) via high-energy UV irradiation physically shatters the boundary, un-freezing the Orthomatter back into chaotic lattice noise.

\section{Conclusion and LVK Consistency}\label{sec:conclusion}
LIGO-Virgo-KAGRA (LVK) observations have ruled out bulk parity violation in propagating gravitational waves. This experiment is explicitly designed to remain consistent with LVK. The parity violation and anomalous pressure we predict occur \emph{strictly at the boundary condition} (the Weyl semimetals) and do not require free-space birefringence. Falsifying or confirming the $+262.5\%$ Casimir anomaly will serve as the definitive laboratory test of the Protoreal topology.



\input{../local_bibs/local_bib_10_chiral_casimir_experiment}
\end{document}
