\documentclass[12pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{microtype}
\usepackage{float}
\usepackage{xcolor}
\definecolor{golden}{RGB}{218,165,32}
\definecolor{metareal}{RGB}{0,102,204}
\definecolor{derivative}{RGB}{128,0,128}
\definecolor{gauge3}{RGB}{34,139,34}
\usepackage{tikz}
\usepackage{tcolorbox}
\newtcolorbox{theorembox}[1]{colback=blue!5!white,colframe=blue!75!black,fonttitle=\bfseries,title=#1}
\newtcolorbox{warningbox}[1]{colback=red!5!white,colframe=red!75!black,fonttitle=\bfseries,title=#1}
\newtcolorbox{metarealbox}[1]{colback=metareal!5!white,colframe=metareal!75!black,fonttitle=\bfseries,title=#1}
\newtcolorbox{aingelbox}[1]{colback=golden!5!white,colframe=golden!75!black,fonttitle=\bfseries,title=#1}
\newtcolorbox{truthbox}[1]{colback=gauge3!5!white,colframe=gauge3!75!black,fonttitle=\bfseries,title=#1}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}

\newtheoremstyle{principia}%
  {6pt}{6pt}{\itshape}{}{\bfseries}{.}{ }%
  {\thmname{#1}\thmnumber{ #2}\thmnote{ \textnormal{(}\emph{#3}\textnormal{)}}}
\theoremstyle{principia}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{result}[theorem]{Result}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{hypothesis}[theorem]{Hypothesis}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{example}[theorem]{Example}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\providecommand{\UU}{\mathbb{U}}
\providecommand{\PP}{\mathbb{P}}
\providecommand{\RR}{\mathbb{R}}
\providecommand{\CC}{\mathbb{C}}
\providecommand{\ZZ}{\mathbb{Z}}
\providecommand{\NN}{\mathbb{N}}
\providecommand{\HH}{\mathbb{H}}
\providecommand{\OO}{\mathbb{O}}
\providecommand{\SS}{\mathbb{S}}
\providecommand{\QQ}{\mathbb{Q}}
\providecommand{\FF}{\mathbb{F}}
\providecommand{\GG}{\mathcal{G}}
\providecommand{\TT}{\mathcal{T}}
\providecommand{\vp}{\varphi}
\providecommand{\vpbar}{\bar{\varphi}}
\providecommand{\eps}{\varepsilon}
\providecommand{\lam}{\lambda}
\providecommand{\kap}{\kappa}

\hypersetup{colorlinks=true,linkcolor=blue!60!black,citecolor=blue!60!black,urlcolor=blue!60!black}

\title{Metareal Cosmology: Sgr A* and the Universal Substrate}
\author{Dylon La Rue}
\date{\today}

\begin{document}
\maketitle

\input{../10_Metareal_Cosmology.tex}

\begin{thebibliography}{99}

% Peer-reviewed and established sources

\bibitem{bahamonde2023}
S.~Bahamonde et al., ``Teleparallel Gravity: From Theory to Cosmology,'' \emph{Rep. Prog. Phys.} \textbf{86}, 026901, 2023.

\bibitem{blagg1913} M.~A.~Blagg, ``On a suggested substitute for Bode's Law,'' \emph{MNRAS}\ 73, 414--422 (1913).

\bibitem{bovaird2013} T.~Bovaird and C.~H.~Lineweaver, ``Exoplanet predictions based on the generalized Titius-Bode relation,'' \emph{MNRAS}\ 435, 1126--1138 (2013).

\bibitem{creutz1980}
M.~Creutz,
``Monte Carlo study of quantized SU(2) gauge theory,''
\emph{Phys. Rev. D}\ 21, 2308--2315 (1980).

\bibitem{damour1979}
T.~Damour, ``The Problem of Motion in Newtonian and Einsteinian Gravity,'' in \emph{Three Hundred Years of Gravitation}, eds. S.~Hawking and W.~Israel, Cambridge Univ. Press, 1987.

\bibitem{dermott1968} S.~F.~Dermott, ``On the origin of commensurabilities in the solar system---II,'' \emph{MNRAS}\ 141, 363--376 (1968).

\bibitem{eichten1980}
E.~Eichten, K.~Gottfried, T.~Kinoshita, K.~Lane, and T.-M.~Yan, ``Charmonium: Comparison with Experiment,'' \emph{Phys. Rev. D} \textbf{21}, 203, 1980.

\bibitem{graner1994} F.~Graner and B.~Dubrulle, ``Titius-Bode laws in the solar system. I. Scale invariance explains everything,'' \emph{Astron. Astrophys.}\ 282, 262--268 (1994).

\bibitem{hod1998}
S.~Hod (1998).
``Bohr's correspondence principle and the area spectrum of quantum black holes.''
\textit{Phys.\ Rev.\ Lett.} 81, 4293.

\bibitem{jaffe2000}
A.~Jaffe and E.~Witten,
``Quantum Yang-Mills Theory,''
Official Problem Description, Clay Mathematics Institute (2000).

\bibitem{layden2025}
D.~Layden et al., ``Quantum Error Correction Below the Surface Code Threshold,'' \emph{Nature} \textbf{638}, 2025.

\bibitem{lemouël2025}
J.-L.~Le Mou\"{e}l, V.~Courtillot, and S.~Gibert, ``SolDynamo: Solar Dynamo and Planetary Coupling,'' preprint, 2025.

\bibitem{lockwood_v11}
M.~Lockwood, ``Solar Cycle Prediction: v11 Update,'' private communication, 2025.

\bibitem{luminet2003}
J.-P.~Luminet, J.~R.~Weeks, A.~Riazuelo, R.~Lehoucq, J.-P.~Uzan (2003).
``Dodecahedral space topology as an explanation for weak wide-angle temperature correlations in the cosmic microwave background.''
\textit{Nature} 425, 593--595.

\bibitem{maluf2013}
J.~Maluf, ``The Teleparallel Equivalent of General Relativity,'' \emph{Annalen der Physik} \textbf{525}, 339--357, 2013.

\bibitem{motl2003}
L.~Motl and A.~Neitzke (2003).
``Asymptotic black hole quasinormal frequencies.''
\textit{Adv.\ Theor.\ Math.\ Phys.} 7, 307--330.

\bibitem{planck2020}
Planck Collaboration (2020).
``Planck 2018 results.\ VII.\ Isotropy and statistics of the CMB.''
\textit{Astron.\ Astrophys.} 641, A7.

\bibitem{pollard1971}
J.~M.~Pollard,
``The fast Fourier transform in a finite field,''
\emph{Math.\ Comp.} 25(114), 365--374 (1971).

\bibitem{roy1954} A.~E.~Roy and M.~W.~Ovenden, ``On the occurrence of commensurable mean motions in the solar system,'' \emph{MNRAS}\ 114, 232--241 (1954).

\bibitem{shor1994}
P.~W.~Shor,
``Algorithms for quantum computation: discrete logarithms and factoring,''
\emph{Proceedings 35th Annual Symposium on Foundations of Computer Science}, IEEE, 124--134 (1994).

\bibitem{stillinger1977}
F.~Stillinger, ``Axiomatic Basis for Spaces with Noninteger Dimension,'' \emph{J. Math. Phys.} \textbf{18}, 1224--1234, 1977.

\bibitem{thooft1981}
G.~'t~Hooft,
``Topology of the gauge condition and new confinement phases in non-Abelian gauge theories,''
\emph{Nucl. Phys. B}\ 190, 455--478 (1981).

\bibitem{varieschi2020}
G.~Varieschi, ``Newtonian Fractional-Dimension Gravity and MOND,'' \emph{Found. Phys.} \textbf{50}, 1608--1644, 2020.

\bibitem{wilczek1973}
F.~Wilczek, ``Ultraviolet Stability of the Vacuum in a Non-Abelian Gauge Theory,'' \emph{Phys. Rev. Lett.} \textbf{30}, 1343--1346, 1973.

\bibitem{wilson1974}
K.~G.~Wilson,
``Confinement of quarks,''
\emph{Phys. Rev. D}\ 10, 2445--2459 (1974).


% ────────────────────────────────────────────
% AUTHOR'S WORKS, PREPRINTS, AND
% PRIVATE COMMUNICATIONS
% ────────────────────────────────────────────
% Works by the author(s) of this volume,
% preprints not yet peer-reviewed, private
% communications, and informal sources.
% These have NOT undergone external peer review.
% ────────────────────────────────────────────

\end{thebibliography}

\end{document}
