\documentclass[12pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{microtype}
\usepackage{float}
\usepackage{xcolor}
\definecolor{golden}{RGB}{218,165,32}
\definecolor{metareal}{RGB}{0,102,204}
\definecolor{derivative}{RGB}{128,0,128}
\definecolor{gauge3}{RGB}{34,139,34}
\usepackage{tikz}
\usepackage{tcolorbox}
\newtcolorbox{theorembox}[1]{colback=blue!5!white,colframe=blue!75!black,fonttitle=\bfseries,title=#1}
\newtcolorbox{warningbox}[1]{colback=red!5!white,colframe=red!75!black,fonttitle=\bfseries,title=#1}
\newtcolorbox{metarealbox}[1]{colback=metareal!5!white,colframe=metareal!75!black,fonttitle=\bfseries,title=#1}
\newtcolorbox{aingelbox}[1]{colback=golden!5!white,colframe=golden!75!black,fonttitle=\bfseries,title=#1}
\newtcolorbox{truthbox}[1]{colback=gauge3!5!white,colframe=gauge3!75!black,fonttitle=\bfseries,title=#1}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}

\newtheoremstyle{principia}%
  {6pt}{6pt}{\itshape}{}{\bfseries}{.}{ }%
  {\thmname{#1}\thmnumber{ #2}\thmnote{ \textnormal{(}\emph{#3}\textnormal{)}}}
\theoremstyle{principia}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{result}[theorem]{Result}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{hypothesis}[theorem]{Hypothesis}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{example}[theorem]{Example}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\providecommand{\UU}{\mathbb{U}}
\providecommand{\PP}{\mathbb{P}}
\providecommand{\RR}{\mathbb{R}}
\providecommand{\CC}{\mathbb{C}}
\providecommand{\ZZ}{\mathbb{Z}}
\providecommand{\NN}{\mathbb{N}}
\providecommand{\HH}{\mathbb{H}}
\providecommand{\OO}{\mathbb{O}}
\providecommand{\SS}{\mathbb{S}}
\providecommand{\QQ}{\mathbb{Q}}
\providecommand{\FF}{\mathbb{F}}
\providecommand{\GG}{\mathcal{G}}
\providecommand{\TT}{\mathcal{T}}
\providecommand{\vp}{\varphi}
\providecommand{\vpbar}{\bar{\varphi}}
\providecommand{\eps}{\varepsilon}
\providecommand{\lam}{\lambda}
\providecommand{\kap}{\kappa}

\hypersetup{colorlinks=true,linkcolor=blue!60!black,citecolor=blue!60!black,urlcolor=blue!60!black}

\title{Markets as Fluid Systems: The Black-Scholes--Navier-Stokes Bridge}
\author{Dylon La Rue}
\date{\today}

\begin{document}
\maketitle

\input{../15_Markets_Fluid_Systems.tex}

\begin{thebibliography}{99}

% Peer-reviewed and established sources

\bibitem{arrow1950}
K.~J.~Arrow,
``A Difficulty in the Concept of Social Welfare,''
\emph{Journal of Political Economy}, vol.~58, no.~4, pp.~328--346, 1950.

\bibitem{btc_indicator2025}
Various,
``Bitcoin as a Leading Indicator for Risk Appetite: 24/7 Liquidity Signals and Equity Market Correlation,''
Market microstructure research and institutional reports, 2024--2026.

\bibitem{crashbenchmark2024}
Various,
``Stock Market Crash Prediction: Evaluation Metrics and Model Comparison,''
Academic surveys across machine learning and econometric approaches, 2020--2024.
Typical precision for 3-month crash prediction: $\sim$15\% at recall $\sim$59\%.

\bibitem{eckerli2021}
F.~Eckerli and J.~Osterrieder,
``Generative Adversarial Networks in Finance: An Overview,''
\emph{arXiv:2106.06364}, 2021.

\bibitem{ewsbenchmark2024}
Various,
``Machine Learning Early Warning Systems for Financial Crises,''
Studies from Bank of Canada, ECB, IMF, and academic papers, 2020--2026.
State-of-the-art AUROC: 0.75--0.88 for 6-month recession forecasting using 15--50 macroeconomic indicators.

\bibitem{fingan2024}
Man AHL Research,
``Fin-GAN: Forecasting and Simulating Financial Time Series with Generative Adversarial Networks,''
\emph{Man Group Research Papers}, 2024.

\bibitem{gabor1946}
D.~Gabor,
``Theory of Communication,''
\emph{Journal of the Institution of Electrical Engineers}, vol.~93, no.~26, pp.~429--457, 1946.

\bibitem{gans_diffusion2024}
Various,
``GAN-Guided Diffusion Models for Financial Time Series,''
\emph{arXiv preprints}, 2024--2025.

\bibitem{gibbard1973}
A.~Gibbard,
``Manipulation of Voting Schemes: A General Result,''
\emph{Econometrica}, vol.~41, no.~4, pp.~587--601, 1973.

\bibitem{hci_prompt2025}
Various,
``Human-Computer Interaction in Financial Trading Systems: Market Research and Design Principles,''
Industry reports and academic surveys, 2025--2026.

\bibitem{hull2018}
J.~C.~Hull,
\emph{Options, Futures, and Other Derivatives},
10th ed., Pearson, 2018.

\bibitem{ilinski1997}
K.~Ilinski,
``Physics of Finance,''
\emph{arXiv:hep-th/9710148}, 1997.

\bibitem{lopezdeprado2018}
M.~L\'{o}pez de Prado,
\emph{Advances in Financial Machine Learning},
Wiley, 2018.
Chapter 11: ``The Dangers of Backtesting.'' Sustained precision above 50\% on crash classification tasks invites scrutiny for look-ahead bias and data leakage.

\bibitem{mandelbrot1963}
B.~B.~Mandelbrot,
``The Variation of Certain Speculative Prices,''
\emph{The Journal of Business}, vol.~36, no.~4, pp.~394--419, 1963.

\bibitem{manton2002}
N.~S.~Manton,
``Fluid mechanical models of financial markets,''
Working paper, DAMTP Cambridge, 2002.

\bibitem{satterthwaite1975}
M.~A.~Satterthwaite,
``Strategy-Proofness and Arrow's Conditions,''
\emph{Journal of Economic Theory}, vol.~10, no.~2, pp.~187--217, 1975.

\bibitem{takahashi2019}
S.~Takahashi, Y.~Chen, and K.~Tanaka-Ishii,
``Modeling Financial Time-Series with Generative Adversarial Networks,''
\emph{Physica A: Statistical Mechanics and its Applications}, vol.~527, 121261, 2019.

\bibitem{timegan2019}
J.~Yoon, D.~Jarrett, and M.~van der Schaar,
``Time-series Generative Adversarial Networks,''
\emph{Advances in Neural Information Processing Systems (NeurIPS)}, 2019.

\bibitem{ttsgan2024}
X.~Li, V.~Metsis, H.~Wang, and A.~Ngu,
``TTS-GAN: A Transformer-based Time-Series Generative Adversarial Network,''
\emph{arXiv:2202.02691v3}, 2024.

\end{thebibliography}

\end{document}
