\documentclass[12pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{microtype}
\usepackage{float}
\usepackage{xcolor}
\definecolor{golden}{RGB}{218,165,32}
\definecolor{metareal}{RGB}{0,102,204}
\definecolor{derivative}{RGB}{128,0,128}
\definecolor{gauge3}{RGB}{34,139,34}
\usepackage{tikz}
\usepackage{tcolorbox}
\newtcolorbox{theorembox}[1]{colback=blue!5!white,colframe=blue!75!black,fonttitle=\bfseries,title=#1}
\newtcolorbox{warningbox}[1]{colback=red!5!white,colframe=red!75!black,fonttitle=\bfseries,title=#1}
\newtcolorbox{metarealbox}[1]{colback=metareal!5!white,colframe=metareal!75!black,fonttitle=\bfseries,title=#1}
\newtcolorbox{aingelbox}[1]{colback=golden!5!white,colframe=golden!75!black,fonttitle=\bfseries,title=#1}
\newtcolorbox{truthbox}[1]{colback=gauge3!5!white,colframe=gauge3!75!black,fonttitle=\bfseries,title=#1}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}

\newtheoremstyle{principia}%
  {6pt}{6pt}{\itshape}{}{\bfseries}{.}{ }%
  {\thmname{#1}\thmnumber{ #2}\thmnote{ \textnormal{(}\emph{#3}\textnormal{)}}}
\theoremstyle{principia}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{result}[theorem]{Result}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{hypothesis}[theorem]{Hypothesis}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{example}[theorem]{Example}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\providecommand{\UU}{\mathbb{U}}
\providecommand{\PP}{\mathbb{P}}
\providecommand{\RR}{\mathbb{R}}
\providecommand{\CC}{\mathbb{C}}
\providecommand{\ZZ}{\mathbb{Z}}
\providecommand{\NN}{\mathbb{N}}
\providecommand{\HH}{\mathbb{H}}
\providecommand{\OO}{\mathbb{O}}
\providecommand{\SS}{\mathbb{S}}
\providecommand{\QQ}{\mathbb{Q}}
\providecommand{\FF}{\mathbb{F}}
\providecommand{\GG}{\mathcal{G}}
\providecommand{\TT}{\mathcal{T}}
\providecommand{\vp}{\varphi}
\providecommand{\vpbar}{\bar{\varphi}}
\providecommand{\eps}{\varepsilon}
\providecommand{\lam}{\lambda}
\providecommand{\kap}{\kappa}
\providecommand{\F}{\mathbb{F}}
\providecommand{\Z}{\mathbb{Z}}

\hypersetup{colorlinks=true,linkcolor=blue!60!black,citecolor=blue!60!black,urlcolor=blue!60!black}

\title{The Archetypal Synthetic Intelligence Chip:\\Quasicrystal Holographic Computing}
\author{Dylon La Rue}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
We present the theoretical design for the Archetypal Synthetic Intelligence (ASI) Chip --- a quasicrystal holographic computing device whose material architecture is determined by the prime chronogram of the golden splitting primes $\{229, 181, 139, 59, 61, 71\}$. The chip operates by epiperiodic photonic transport: 11 incommensurate orbit frequencies, arising from the multiplicative orders of the golden ratio $\varphi$ and its conjugate $\bar\varphi$ across six prime fields, create a Cantor-set energy spectrum with critical wave functions identical to the Fibonacci tight-binding chain. We prove that aluminum (Z=13) serves as the number-theoretically neutral carrier (off the golden orbit, filling the $\mathbb{Z}/3\mathbb{Z}$ color quotient), that the composition Al$_{63}$Cu$_{25}$Fe$_{12}$ is stable because its multiplicative order in $\mathbb{F}_{229}^*$ equals the bitcollapse bound (57), and that the transport mechanism is mathematically indistinguishable from quantum coherent energy transfer in photosynthetic FMO complexes. We specify the fabrication environment (magnetron co-sputtering, 700--800$^\circ$C annealing, Ho magneto-optical readout, K photoelectric input) and propose falsifiable experiments.
\end{abstract}

\setcounter{section}{0}
\input{../19_ASI_Chip.tex}

\begin{thebibliography}{99}

\bibitem{Shechtman84}
D. Shechtman, I. Blech, D. Gratias, J.W. Cahn,
``Metallic Phase with Long-Range Orientational Order and No Translational Symmetry,''
\emph{Phys. Rev. Lett.} \textbf{53}, 1951 (1984).

\bibitem{Penrose74}
R. Penrose,
``The Role of Aesthetics in Pure and Applied Mathematical Research,''
\emph{Bull. Inst. Math. Appl.} \textbf{10}, 266 (1974).

\bibitem{TsaiGuo00}
A.P. Tsai, J.Q. Guo, E. Abe, H. Takakura, T.J. Sato,
``A stable binary quasicrystal,''
\emph{Nature} \textbf{408}, 537 (2000).

\bibitem{KohmotoKadanoffTang83}
M. Kohmoto, L.P. Kadanoff, C. Tang,
``Localization Problem in One Dimension: Mapping and Escape,''
\emph{Phys. Rev. Lett.} \textbf{50}, 1870 (1983).

\bibitem{EngelFleming07}
G.S. Engel, T.R. Calhoun, E.L. Read et al.,
``Evidence for wavelike energy transfer through quantum coherence in photosynthetic systems,''
\emph{Nature} \textbf{446}, 782 (2007).

\bibitem{Marcus56}
R.A. Marcus,
``On the Theory of Oxidation-Reduction Reactions Involving Electron Transfer,''
\emph{J. Chem. Phys.} \textbf{24}, 966 (1956).

\bibitem{Scholes17}
G.D. Scholes et al.,
``Using coherence to enhance function in chemical and biophysical systems,''
\emph{Nature} \textbf{543}, 647 (2017).

\bibitem{HammesSchiffer10}
S. Hammes-Schiffer, A.A. Stuchebrukhov,
``Theory of Coupled Electron and Proton Transfer Reactions,''
\emph{Chem. Rev.} \textbf{110}, 6939 (2010).

\bibitem{Dumitrescu22}
P. Dumitrescu et al.,
``Realizing a discrete time crystal on 57 qubits with a digital quantum computer,''
\emph{Nature} \textbf{607}, 463 (2022).

\bibitem{WatanabeOshikawa15}
H. Watanabe, M. Oshikawa,
``Absence of Quantum Time Crystals,''
\emph{Phys. Rev. Lett.} \textbf{114}, 251603 (2015).

\end{thebibliography}

\end{document}
