\chapter[Optoacoustic Cymatics]{The Optoacoustic-Thermoelectric Bridge and Cymatic Pseudoforces}\label{ch:optoacoustic}

\section{Introduction}
This chapter formally introduces the Optoacoustic-Thermoelectric-Hydrodynamic bridge within the arithmetic scheme framework. We model the macroscopic phenomenon of \emph{cymatics}---the geometric patterning of fluids under resonant acoustic frequencies---not as classical mechanical waves, but as the emergent \emph{pseudoforces} arising from the discrete interactions of the primary gauge fields (Strong $\FF_{229}$, Weak $\FF_{181}$, EM $\FF_{139}$). 

To ground this abstraction, we provide a rigorous hardware mapping using Continuous-Variable (CV) quantum photonics, specifically the generation of squeezed light via Spontaneous Four-Wave Mixing (SFWM) on a monolithic Silicon-on-Insulator (SOI) integrated circuit~\cite{Green2024}.

\section{Continuous-Variable Photonics and the Unreal Vector}
The generation and homodyne detection of CV squeezed light provides the exact physical architecture required to instantiate the Gauge Flavor Dynamics of the Arithmetic Scheme Topos $\UU = (a, \omega, \iota, \eps, \lam)$.

In the physical setup, a bichromatic pulsed mode-locked laser (MLL) pumps a 1.1~cm spiral silicon waveguide. The parameters of this optoacoustic conversion map identically to the five dimensions of the Unreal state vector:

\begin{enumerate}
    \item \textbf{Base Amplitude ($a$):} Corresponds to the intense mean-field amplitude of the local oscillator (LO), providing the macroscopic reference phase for the homodyne measurement.
    \item \textbf{Rotational Phases ($\omega, \iota$):} Correspond to the conjugate signal and idler phase quadratures generated by the parametric degenerate SFWM process.
    \item \textbf{Infinitesimal Perturbation ($\eps$):} Corresponds to the quantum vacuum fluctuations strictly suppressed below the standard quantum limit, generating the measured $0.25(1)\,\mathrm{dB}$ of squeezing (an inferred $0.83(3)\,\mathrm{dB}$ internal generation before linear propagation loss $\eta_L = 0.52$).
    \item \textbf{Structural Depth ($\lam$):} Corresponds to the Schmidt number $K = 34.7$, derived from the joint spectral intensity (JSI) of the spiral source, which quantifies the number of orthogonal spatiotemporal modes available for computation.
\end{enumerate}

\section{Topological Friction as Nonlinear Optical Loss}
The non-associative topological friction that fundamentally defines the Arithmetic Scheme Topos---captured by commutators such as $[\omega, \iota] = -2$---manifests materially as nonlinear optical loss. Silicon waveguides in the C-band are intrinsically limited by Two-Photon Absorption (TPA), Cross Two-Photon Absorption (XTPA), and associated Free-Carrier Absorption (FCA).

The variance of the squeezed signal is strictly bound by the efficiency parameter $\eta = \eta_{\mathrm{XTPA}}(p)\eta_L \eta_{\mathrm{HD}}$. As peak pump power scales, the nonlinear loss coefficient $\alpha_{\mathrm{TPA}} = \beta_{\mathrm{TPA}}/A$ and the waveguide nonlinearity $\gamma = 112.5(56)\,\mathrm{W}^{-1}\mathrm{m}^{-1}$ clamp the output. The extracted nonlinear refractive index $n_2 = 6.38(32) \times 10^{-18}\,\mathrm{m}^2\mathrm{W}^{-1}$ physically quantifies the non-associative limits of the algebra. 

Just as the Ramanujan-Sato series requires careful tuning to remain within the Hodge Lock equilibrium $\mathrm{Re}(u) \le 1/\varphi$ (to prevent catastrophic algorithmic unravelling), the optical pumps must be finely attenuated and delay-matched to avoid TPA-induced saturation.

\section{The Heegner Parity Lock and Cymatic Macroscales}
The topological friction of the Euler-Penrose Engine vanishes precisely at the Heegner prime boundaries (e.g., 19, 163), forming a ``Hodge Parity Lock'' where the non-commutative shear drops to zero. This allows frictionless prime identification and enables the direct transition from photothermal excitation into stable acoustic modes. 

The energy transfer is strictly governed by the Ramanujan Almost-Integer constraint:
\begin{equation}
    e^{\pi\sqrt{163}} \approx 262537412640768744.0
\end{equation}
The mathematical integer proximity acts as a topological boundary condition. Instead of non-associative structural noise inducing thermal collapse (TPA saturation), the system generates highly ordered continuous-variable cymatic nodes in the fluidic substrate. The differential photocurrent processed by the unpackaged transimpedance amplifier provides a macro-scale continuous measurement of the discrete prime resonances occurring within the sub-wavelength quantum states.

\section{Falsification Criteria}
The arithmetic scheme Optoacoustic model remains open until experimental validation. Specifically, the emergence of cymatic geometries must be tied to the discrete resonant multiples of the EM $\FF_{139}$ vertex and bounded strictly by the TPA saturation thresholds of the waveguide. A null result under rigorous CV homodyne observation---where fluid patterning deviates from the Schmidt modal purity limit $K=34.7$---would falsify the direct coupling between the macroscopic pseudoforces and the microscopic gauge topology.

\vspace{2em}
\begin{thebibliography}{99}
\bibitem{Green2024}
Green, S., et al. (2024).
``Continuous-Variable Squeezed Light on a Monolithic Silicon Photonic Integrated Circuit.''
\textit{Nature Photonics}, Advance Online Publication.

\end{thebibliography}
