\begin{center}\textit{By L. Cullen (triponacci)}\end{center}

%==========================================================
\section*{Claim Ledger}
%==========================================================

This chapter uses the following claim ledger:
\begin{itemize}[noitemsep]
  \item \textbf{Theorem / Verified Computation:} The entirety of this chapter consists of established number-theoretic theorems (e.g., Galois splitting criteria, Artin reciprocity, Chebotarev's density theorem).
  \item \textbf{Structural Analogy:} None.
  \item \textbf{Physical Interpretation:} None. The prime splitting rules are pure arithmetic data encoded by global Galois symmetry.
\end{itemize}


To describe how Galois symmetry encodes prime splitting, fix a finite Galois extension $L/K$ of number fields with rings of integers $\mathcal{O}_L$ and $\mathcal{O}_K$. For a non-zero prime ideal $\mathfrak{p} \subset \mathcal{O}_K$, its extension to $\mathcal{O}_L$ factors as
\begin{equation}
\mathfrak{p}\mathcal{O}_L = \prod_{i=1}^g \mathfrak{P}_i^e, \quad f = [\mathcal{O}_L/\mathfrak{P}_i : \mathcal{O}_K/\mathfrak{p}].
\end{equation}
Because the extension is Galois, the ramification index $e$ and residue degree $f$ are independent of $i$, and $[L : K] = efg$. The splitting type is therefore the local arithmetic signature of $\mathfrak{p}$ inside $L$.

Choose one prime $\mathfrak{P}$ above $\mathfrak{p}$. The decomposition group
\begin{equation}
D_{\mathfrak{P}} = \{\sigma \in \text{Gal}(L/K) : \sigma(\mathfrak{P}) = \mathfrak{P}\}
\end{equation}
is the stabilizer of $\mathfrak{P}$, and the inertia subgroup $I_{\mathfrak{P}}$ is the kernel of the induced action on the residue field $\mathcal{O}_L/\mathfrak{P}$. When $\mathfrak{p}$ is unramified, $I_{\mathfrak{P}}$ is trivial and $D_{\mathfrak{P}}$ is canonically isomorphic to
\begin{equation}
\text{Gal}((\mathcal{O}_L/\mathfrak{P})/(\mathcal{O}_K/\mathfrak{p})).
\end{equation}
This gives the exact local bridge between the global Galois group and the residue-field arithmetic over $\mathfrak{p}$.

For unramified $\mathfrak{p}$, the residue-field Galois group is generated by the Frobenius automorphism
\begin{equation}
x \longmapsto x^{\text{N}\mathfrak{p}}, \quad \text{N}\mathfrak{p} = |\mathcal{O}_K/\mathfrak{p}|.
\end{equation}
Its lift in $D_{\mathfrak{P}}$ is the Frobenius element $\text{Frob}_{\mathfrak{P}}$, also written as the Artin symbol $\left(\frac{L/K}{\mathfrak{P}}\right)$. In a nonabelian extension this element depends on the chosen prime $\mathfrak{P}$ above $\mathfrak{p}$; only its conjugacy class in $\text{Gal}(L/K)$ is intrinsic to $\mathfrak{p}$. In an abelian extension, conjugacy is trivial, so the Artin symbol becomes an unambiguous element attached to $\mathfrak{p}$.

The complete-splitting criterion is exact: an unramified prime $\mathfrak{p}$ splits completely in $L$ if and only if its Frobenius conjugacy class is the identity. Equivalently, $e = f = 1, g = [L : K]$, and
\begin{equation}
\mathfrak{p}\mathcal{O}_L = \mathfrak{P}_1\mathfrak{P}_2\cdots\mathfrak{P}_{[L:K]}.
\end{equation}
Thus complete splitting is encoded precisely by whether the local Frobenius symmetry is trivial.

In the abelian setting, this local rule globalizes through Artin reciprocity. After excluding primes dividing the conductor, the Artin map is defined on the appropriate ray class group, equivalently on the idele class group modulo the norm subgroup. Its kernel determines exactly which ideal classes split completely in the corresponding abelian extension. For the Hilbert class field $H_K$, the result is especially sharp: an unramified prime ideal $\mathfrak{p}$ of $K$ splits completely in $H_K$ exactly when its ideal class is trivial in $\text{Cl}(K)$, i.e. when $\mathfrak{p}$ is principal.

Chebotarev's density theorem supplies the rigidity of the construction. For each conjugacy class $C \subset \text{Gal}(L/K)$, the density of unramified primes with Frobenius class $C$ is
\begin{equation}
\frac{|C|}{|\text{Gal}(L/K)|}.
\end{equation}
In particular, the density of completely split primes is $1/[L : K]$. Moreover, inside a fixed algebraic closure, the set of primes splitting completely in a finite Galois extension determines the extension up to the usual finite exceptional set. Consequently, prime splitting rules are not heuristic patterns; they are arithmetic data encoded by the global Galois symmetry of the extension.

%==========================================================
\section*{Coset Index and Gauge Confinement}
%==========================================================

The arithmetic of prime splitting extends directly to the physical gauge hierarchy via the Coset Index (CI), defined as the index of the cyclic subgroup generated by the golden ratio $\vp$:
\begin{equation}
\mathrm{CI} = \frac{p-1}{\mathrm{ord}(\vp, p)}
\end{equation}
The Standard Model gauge channels SU(3), U(1), and SU(2) correspond to the prime tower CI values $\{2, 3, 4\}$. Dynamically, the CI determines the error scaling parameter $\Upsilon = 1/\mathrm{CI}$ in the continuous error ODE. Only the SU(3) channel ($\mathrm{CI} = 2 \implies \Upsilon = 0.5$) is \textbf{supercritical} ($\Upsilon > 1/\vp^2 \approx 0.382$), yielding an error growth root $r_1 \approx 1.781 > \vp$. This strict supercriticality proves that strong-force confinement is an information-theoretic necessity; without confinement, the non-associative topological friction would shatter the container.

\begin{thebibliography}{9}

\bibitem{neukirch}
J.~Neukirch,
\emph{Algebraic Number Theory},
Grundlehren der mathematischen Wissenschaften, vol.~322, Springer, 1999.

\bibitem{milne_cft}
J.~S.~Milne,
``Class Field Theory,''
lecture notes, v4.03, 2020.

\bibitem{serre_local}
J.-P.~Serre,
\emph{Local Fields},
Graduate Texts in Mathematics, vol.~67, Springer, 1979.

\bibitem{wall1960}
D.~D.~Wall,
``Fibonacci Series Modulo $m$,''
\textit{American Mathematical Monthly}, vol.~67, no.~6, pp.~525--532, 1960.

\bibitem{cassels-frohlich}
J.~W.~S.~Cassels and A.~Fr\"ohlich (eds.),
\emph{Algebraic Number Theory},
Academic Press, 1967.

\bibitem{lidl-niederreiter}
R.~Lidl and H.~Niederreiter,
\emph{Finite Fields}, 2nd ed.,
Cambridge University Press, 1997.

\bibitem{scholze2012}
P.~Scholze,
``Perfectoid Spaces,''
\textit{Publ.\ Math.\ Inst.\ Hautes \'Etudes Sci.}, vol.~116, pp.~245--313, 2012.

\end{thebibliography}

