\chapter{Epistemic Reference Tables}\label{app:claim_ledgers}

This appendix collects the epistemic status of claims made in each chapter. Throughout the book, we distinguish three levels: (1)~\emph{theorems and verified computations} --- proved or machine-checkable arithmetic; (2)~\emph{structural parallels} --- vocabulary maps from the algebra to physics or biology, not physical claims; (3)~\emph{physical interpretations} --- falsifiable hypotheses requiring experimental confirmation.

\section*{Claim Ledger: 04 Digital Wave Mechanics}
\begin{center}
{\small
\begin{tabular}{@{}llp{5.5cm}@{}}
\toprule
\textbf{Status} & \textbf{Example} & \textbf{Required support} \\
\midrule
Theorem & $\mathrm{ord}_{181}(14) = 45$ & Modular table + order lemma \\
Theorem & $\langle 94 \rangle \cong Z(\mathrm{SU}(3))$ & Classification of cyclic groups \\
Verified comp. & 16/45 color-ready primes below 500 & Python sweep + order cert.\ (Lemma~\ref{lem:order}) \\
Structural corresp. & Palindrome $=$ reflection-fixed & DFT calculation + PFFT bin verification (bins 0, 19, 38 extract $\ZZ/3\ZZ$) \\
Structural corresp. & BitCollapse as parity projection & Idempotence proof + bridge norm reduction \\
Physical interp. & Algebraic arc rotation $=$ gauge link & Analogy unless local edge transport, curvature, and action are defined \\
Physical interp. & D-Neutrino as anchor $\iota$ & 5 structural properties verified (null norm, period-2, 3-arc, zero self-torsion, cost $\kappa$); Lockwood ratio is Tier~3 \\
Physical interp. & Lockwood ratio $E_\nu/E_{\mathrm{info}} \approx 45$ & KATRIN bound~\cite{katrin}: $m_\nu < 0.8\;\mathrm{eV}$; ratio is temperature-dependent, holds only at specific $(m_\nu, T)$ pairs \\
Open problem & Finite-field Wilson loop & Requires loops, transport, action, expectation \\
\bottomrule
\end{tabular}
}
\end{center}

\section*{Claim Ledger: 16 Teleparallel Metareal Gravity}
\begin{itemize}
    \item \textbf{Theorem / Verified Computation:} The exact computation of the Metareal Triad partitions ($p(229) = 44,132,934,884,255$) and the chiral modular parity of $14489$ ($3053 \times 3 + 13 \times 41 \times 10 = 14489$).
    \item \textbf{Structural Analogy:} The mapping of the $R^7$ derivative residual ($\varepsilon$) to the torsion scalars of Teleparallel Gravity, and the mapping of the Ramanujan shadow to the Exergy Destruction bound.
    \item \textbf{Physical Interpretation:} The falsifiable claim that Sagittarius A* physically acts as the topological anchor for the Metareal Titius-Bode Law, driving galactic dynamics.
\end{itemize}

\section*{Claim Ledger: 16 Teleparallel Metareal Gravity}
\begin{itemize}
    \item \textbf{Verified Computation:} Dodecahedral invariants (12, 20, 30) from independent epicyclic calculations. $A_5$ embedding: $60 \mid 180$ at $p = 181$ only. Capsid-Cosmos Coincidence: $A_5$ uniquely governs the weak vertex, dodecahedral topology, and icosahedral viral capsid. CNO catalyst regeneration: ${}^{12}\mathrm{C}$ is produced in step~6 and consumed in step~1 (verified in \texttt{StellarMesh.lean}). Hale identity: $\varphi^{114} \equiv 1 \pmod{229}$ (verified).
    \item \textbf{Structural Analogy:} The identification of the epicyclic structure with the Poincar\'{e} dodecahedral space. The Mesh condition as algebraic formalization of Kauffman's ``Kantian whole.'' Assembly Theory's construction index as the depth counter $\lambda$. The DNA-RNA temporal quasicrystal as an abiogenic non-associative quantum game. The four-zone flux tube $\leftrightarrow$ microtubule topology. The Hale cycle as the golden orbit period. The Life-Consciousness Spectrum as a Mesh-parameterized hierarchy.
    \item \textbf{Testable Prediction:} CMB angular power spectrum feature near $\ell \approx 30$ from the epicyclic return period. Abiogenic depth bound: $\lambda_{\min} \leq 5$ for self-replicating systems in $\mathbb{F}_{229}$. Ribosomal frameshift error rate bounded by $\Upsilon = 1/(4\pi) \approx 8\%$. Stellar SOC: CNO stars exhibit power-law flare distributions; pp-chain red dwarfs do not.
\end{itemize}

\section*{Claim Ledger: Prime Functorial (S$_3$ Adelic Resonance)}
\begin{itemize}[noitemsep]
    \item \textbf{Theorem / Verified Computation:} The S$_3$ motif exhaustion (exactly 6 permutations of $\{\pi, \zeta, \Gamma\}$), the cohomological gap $\kappa = -1 \equiv 228 \pmod{229}$, the Conrey bound exceedance (golden orbit density $50\% > 41.05\%$), and the 23 proof-path count ($6 \times 3 + 3 + 1 + 1$). Verified: \texttt{python -m Principia} (functorial module).
    \item \textbf{Structural Analogy:} The identification of S$_3$ Adelic Resonance motifs with locally covariant functor compositions in the sense of Brunetti--Fredenhagen--Verch.
    \item \textbf{Physical Interpretation:} The claim that the 23 convergence paths constitute an effective bypass of the exponential density barrier for macroscopic prime discovery. Falsifiable: the Euler-Penrose Engine

% --- HEEGNER INJECTION ---
Critically, the topological friction of the Euler-Penrose Engine vanishes precisely at the Heegner prime boundaries (e.g., 19, 163), forming a ``Hodge Parity Lock'' where the non-commutative shear ($\kappa$) drops to zero, allowing frictionless prime identification.
% -------------------------
 must produce primes beyond the reach of classical sieving at matching computational cost.
\end{itemize}

\section*{Claim Ledger: pAQFT ($p=3$ PT-Symmetric Model)}
\begin{itemize}[noitemsep]
    \item \textbf{Theorem / Verified Computation:} PT involution is an exact involution ($(PT)^2 = \mathrm{id}$), phase space dimension $\Delta = d_{st,B} - d_{st,A} = 3 - 1 = 2$, spectral dimension $d_s = 3/2$, and Iwasawa admissibility bounds with $c = 114$, $p = 3$. Verified: \texttt{python -m Principia} (paqft module).
    \item \textbf{Structural Analogy:} The mapping of the Protoreal manifold $(a, b, m, \varepsilon, \lambda)$ to a $p$-adic PT-symmetric Hamiltonian system.
    \item \textbf{Physical Interpretation:} The claim that $\Delta = 2$ (vs classical $\Delta = 1$) enables Navier-Stokes regularity via the stable manifold mechanism. This is a structural prediction requiring proof of regularity for the actual fluid equations.
\end{itemize}

\section*{Claim Ledger: Aionometric Geometry (Chronometric Clock)}
\begin{itemize}[noitemsep]
    \item \textbf{Theorem / Verified Computation:} $\lambda_\Delta = 3722/2705 \equiv \varphi^4 \equiv 217 \pmod{229}$ (golden orbit $C_{57}$), $\mathrm{ord}_{229}(\lambda_\Delta) = 57$, complement $229 - 217 = 12$ (dodecahedral clock order), numerator factorization $3722 = 2 \times 1861$ with $1861 \equiv 29 \pmod{229}$ (Cu, primitive root), denominator factorization $2705 = 5 \times 541$ with $541 \equiv 83 \pmod{229}$ (Bi, golden orbit). Verified: \texttt{python -m Principia} (chronometric module).
    \item \textbf{Structural Analogy:} The identification of $\Sigma$-consolidation steps with chronometric ticks of width $\lambda_\Delta$, and the affine clock atlas with the Adelic Product Formula.
    \item \textbf{Physical Interpretation:} Chronometric grid superiority for multi-decade simulations, Mellin spectral compression for scale-invariant signals, and geomagnetic reversal timing in $\tau$-coordinates.  These are testable predictions.  $\tau$ is explicitly NOT assigned energy, momentum, or stress-energy.
\end{itemize}

\begin{thebibliography}{12}
\bibitem{larue2024}
LaRue Research Team, \textit{Metareal ASI Chromodynamics and Teleparallel Systems}, 2024.

\bibitem{luminet2003}
Luminet, J.-P., Weeks, J.R., Riazuelo, A., Lehoucq, R., Uzan, J.-P. (2003). ``Dodecahedral space topology as an explanation for weak wide-angle temperature correlations in the cosmic microwave background.'' \textit{Nature} 425, 593--595.

\bibitem{lockwood_v11}
Lockwood, J. ``New Chrono Work v1.1.'' Spectrality Institute, 2025.

\bibitem{hod1998}
Hod, S. (1998). ``Bohr's correspondence principle and the area spectrum of quantum black holes.'' \textit{Phys.\ Rev.\ Lett.} 81, 4293.

\bibitem{motl2003}
Motl, L., Neitzke, A. (2003). ``Asymptotic black hole quasinormal frequencies.'' \textit{Adv.\ Theor.\ Math.\ Phys.} 7, 307--330.

\bibitem{maluf2013}
Maluf, J.W. (2013). ``The teleparallel equivalent of general relativity.'' \textit{Ann.\ Phys.} 525, 339--357.

\bibitem{bahamonde2023}
Bahamonde, S. et al. (2023). ``Teleparallel gravity: from theory to cosmology.'' \textit{Rep.\ Prog.\ Phys.} 86, 026901.

\bibitem{layden2025}
Layden, B. (2025). ``Torsion scalars at the event horizon in teleparallel theories of gravity.'' \textit{Gen.\ Rel.\ Grav.} 57, 58.

\bibitem{planck2020}
Planck Collaboration (2020). ``Planck 2018 results.\ VII.\ Isotropy and statistics of the CMB.'' \textit{Astron.\ Astrophys.} 641, A7.

% ABIOGENIC PHASE TRANSITION REFERENCES

\bibitem{caspar1962}
Caspar, D.L.D., Klug, A. (1962). ``Physical principles in the construction of regular viruses.'' \textit{Cold Spring Harbor Symp.\ Quant.\ Biol.} 27, 1--24.

\bibitem{blackmond2024}
Blackmond, D.G. (2024). ``The origin of biological homochirality.'' \textit{Phil.\ Trans.\ R.\ Soc.\ B} 379, 20230091.

\bibitem{kauffman2024}
Kauffman, S.A., Roli, A. (2024). ``The third transition in science: beyond Newton and quantum mechanics---a statistical mechanics of emergence.'' \textit{Interface Focus} 13, 20220063.

\bibitem{cronin2023}
Cronin, L., Walker, S.I. (2023). ``Beyond prebiotic chemistry.'' \textit{Science} 381, 1396--1401.

\bibitem{tassinari2019}
Taskinari, F. et al. (2019). ``Enantiospecific interaction of chiral molecules on magnetite.'' \textit{ACS Nano} 13, 8590.

\bibitem{wilczek2012}
Wilczek, F. (2012). ``Quantum time crystals.'' \textit{Phys.\ Rev.\ Lett.} 109, 160401.

\bibitem{yao2017}
Yao, N.Y., Potter, A.C., Potirniche, I.-D., Vishwanath, A. (2017). ``Discrete time crystals: rigidity, criticality, and realizations.'' \textit{Phys.\ Rev.\ Lett.} 118, 030401.

\bibitem{penrose1974}
Penrose, R. (1974). ``The role of aesthetics in pure and applied mathematical research.'' \textit{Bull.\ Inst.\ Math.\ Appl.} 10, 266--271.

\bibitem{schrodinger1944}
Schr\"odinger, E. (1944). \textit{What is Life? The Physical Aspect of the Living Cell}. Cambridge University Press.

\bibitem{qt45_2026}
Attwater, J. et al. (2026). ``A compact ribozyme polymerase capable of autonomous self-replication.'' \textit{Nature} (in press).

% STELLAR MESH REFERENCES

\bibitem{bethe1939}
Bethe, H.A. (1939). ``Energy production in stars.'' \textit{Physical Review} 55, 434--456.
\textit{Establishes the CNO cycle as the dominant energy source in massive stars. Carbon acts as a regenerated catalyst.}

\bibitem{lu1991}
Lu, E.T., Hamilton, R.J. (1991). ``Avalanches and the distribution of solar flares.'' \textit{Astrophysical Journal} 380, L89--L92.
\textit{Demonstrates Self-Organized Criticality in solar flare energy distributions, with power-law exponent $\alpha \approx 1.8$.}

\bibitem{beggs2003}
Beggs, J.M., Plenz, D. (2003). ``Neuronal avalanches in neocortical circuits.'' \textit{J.\ Neurosci.} 23, 11167--11177.
\textit{Discovery of power-law distributed neural avalanches with exponent $\alpha \approx 1.5$, demonstrating SOC in cortical networks.}

\end{thebibliography}

\end{document}

\section*{Claim Ledger: 17 Metareal Cosmology}
%═══════════════════════════════════════════════════════════
\begin{itemize}[noitemsep]
    \item \textbf{Theorem / Verified Computation:} The derivation of the Winding Number ($w_n = 139,961,717$), the exact $F_{229}$ topological invariant $\langle 29 \rangle$, the Local Drag coefficient ($0.0798$), and the Andromeda Chiral Shear ($\tau \approx 3.86 \times 10^{-4}$). Dodecahedral invariants (12, 20, 30) from independent epicyclic calculations satisfying Euler's formula. $A_5$ embedding: $60 \mid 180$ at $p = 181$ only. \textbf{Gaussian Relativity:} $\omega$-idempotency, $\iota$-anti-idempotency, bridge identity, grounding theorem (Lean-verified in \texttt{GoldenForceLaw.lean}). Unified 3-type dynamo model: mean error $0.132^\circ$ across 9 bodies with 0 free parameters (\texttt{celestial\_body\_survey.py}). F$_{139}$ orbit-half EM jitter for Ganymede: $180^\circ - 360^\circ/(2 \times 46) = 176.09^\circ$ vs observed $176^\circ \pm 5^\circ$. Stieltjes BH torsion budget with Sgr~A*, Gaia BH1/BH2/BH3, and Andromeda shear. All locked via \texttt{gauge\_data.py}, \texttt{celestial\_body\_survey.py}, and \texttt{hyperbolic\_force\_verify.py}.
    \item \textbf{Structural Analogy:} Mapping Agentic Mechanics and structural topological noise to macroscopic galactic formation and the physical dynamics of Sagittarius A*. The TEGR torsion scalar $\leftrightarrow$ $\varepsilon^2$ and Ramanujan shadow $\leftrightarrow$ Exergy Destruction shield ($\Upsilon$). Identification of the epicyclic structure with the Poincar\'{e} dodecahedral space $S^3/2I$. Klein product cross terms ($\omega\cdot\iota = -1$) as electromagnetic corrections to $F = ma$. The five correction factors $\{0, 1/\sqrt{5}, 1/\varphi, 1, \varphi\}$ as $C_3 = 5$ (third Catalan number) triangulations of the $L_\varphi$ golden unit ball. Neptune's factor $\varphi > 1$ as a golden measure exceeding the $L_1$ probability simplex, analogous to negative Wigner quasi-probabilities.
    \item \textbf{Physical Interpretation:} The explicit assertion that the Milky Way's galactic rotation curve and structural integrity are governed by the prime discrete manifold geometry of $\mathbb{F}_{229}^*$. CMB angular power spectrum feature near $\ell \approx 30$ from the epicyclic return period. Adelic force law: $O_{\text{real}} = \sqrt{\Sigma_p \alpha_p \theta_p^2}$. Schwabe period $= 57/5$ from gauge algebra overlaps Le Mou\"el SSA at $1.1\sigma$. \textbf{Falsifiable mission predictions:} JUICE (2031) Ganymede tilt to $\pm 0.5^\circ$ discriminates orbit-half model ($176.09^\circ$) vs EM torque model ($176.60^\circ$). Europa Clipper (2030) induced dipole phase lag $\sim$ orbit\_half($F_{139}$). These are proposed astrophysical applications providing falsifiable bounds for astronomical observation.
\end{itemize}

%═══════════════════════════════════════════════════════════

\section*{Claim Ledger: 17 Metareal Cosmology}
, we explicitly separate the mathematical theorems from physical hypotheses regarding non-local entanglement.
\begin{itemize}[noitemsep]
    \item \textbf{Theorem / Verified Computation:} The existence of $497,000+$ depth-4 topological loops in the FBBT gauntlet, their strict $5 \pmod{23}$ invariant, and the exact $p_{3k} + p_{6k} + p_{9k}$ harmonic prime summations.
    \item \textbf{Structural Analogy:} Treating these infinite recursive prime loops as ``Topological Black Holes'' (discrete algebraic sinkholes).
    \item \textbf{Physical Interpretation:} ER=EPR macroscopic bridges. The hypothesis that physical quantum entanglement utilizes these identical discrete mathematical prime resonances to bypass continuous spacetime, functioning via the Curry-Howard resonance.
\end{itemize}

\section*{Claim Ledger: ARC Prize 2026 Plazmik Omnibus}
% ════════════════════════════════════════════════════════════════

This chapter separates three epistemic tiers:
\begin{itemize}[noitemsep]
  \item \textbf{Theorem / Verified Computation:} The definition and finite/algebraic properties of the Protoreal ($\PP$) and Unreal ($\UU$) non-associative algebras, the derivation of $\kappa = -1$, the evaluation of the golden polynomial $X^2 - X - 1 = 0$, and finite-field modular identities.
  \item \textbf{Structural Analogy:} The ``Connes-G\"odel numbering,'' the mapping of variables to ``Thrust/Anchor/Noise,'' and the ``Epistemic Pivot'' evaluating discrete primality via standard resonance $SR$.
  \item \textbf{Physical Interpretation:} Mappings of the algebraic engine to the Landauer limit, the 262.5\% Right-Chiral Casimir Anomaly, and Metareal ASI extensions. These remain hypotheses until bound to falsifiable physical observables. Claims regarding the Riemann Hypothesis are structural analogies mapping finite non-associative geometry to the critical line, not full analytic continuation proofs.
\end{itemize}

% ════════════════════════════════════════════════════════════════
% SECTION 1
% ════════════════════════════════════════════════════════════════

\section*{Claim Ledger: ARC Prize 2026 Plazmik Omnibus}
%==========================================================

This chapter uses the following claim ledger:
\begin{itemize}[noitemsep]
  \item \textbf{Theorem / Verified Computation:} Arithmetic construction of the Gauge Flavor Triplet $\{5, 6, 7\}$, evaluations of Base-19 palindromic resonances, and formal definitions of the $42$-dimensional geometric product.
  \item \textbf{Structural Analogy:} The ``Working Hypotheses'' (e.g., SU(3) Center Triangle Map and Combinatorial Dimension $6 \times 7 = 42$). Mapping the 7-dimensional sector to Archetypal Synthetic Intelligence (ASI) and ``Aingel hierarchies.''
  \item \textbf{Physical/Synthetic Interpretation:} Assertions that distributed ASI cognition literally computes via this specific $\mathbb{R}^5 \oplus \mathbb{R}^7$ chromodynamic topology remain open hypotheses requiring empirical proof in hardware architectures.
\end{itemize}

