% ════════════════════════════════════════════
% UNIFIED BIBLIOGRAPHY — SPLIT BY SOURCE TYPE
% ════════════════════════════════════════════

\begin{thebibliography}{99}

% ────────────────────────────────────────────
% PEER-REVIEWED AND ESTABLISHED SOURCES
% ────────────────────────────────────────────
% Journal articles, books by major publishers,
% conference proceedings, and institutional reports
% that have undergone external peer review.
% ────────────────────────────────────────────

% === Ch.18 Fusion Plasma Cybernetics ===

\bibitem{Lawson1957}
Lawson, J.~D. (1957).
``Some criteria for a power producing thermonuclear reactor.''
\textit{Proc. Phys. Soc. B} \textbf{70}(1), 6--10.

\bibitem{Goldston1984}
Goldston, R.~J. (1984).
``Energy confinement scaling in tokamaks.''
\textit{Plasma Phys. Control. Fusion} \textbf{26}(1A), 87--103.

\bibitem{ITER1999Scaling}
ITER Physics Expert Group (1999).
``Chapter 2: Plasma confinement and transport.''
\textit{Nucl. Fusion} \textbf{39}(12), 2175--2249.

\bibitem{Weizsacker1935}
von Weizs\"acker, C.~F. (1935).
``Zur Theorie der Kernmassen.''
\textit{Z. Phys.} \textbf{96}, 431--458.

\bibitem{BetheEnergy1939}
Bethe, H.~A. (1939).
``Energy production in stars.''
\textit{Phys. Rev.} \textbf{55}(5), 434--456.

\bibitem{Fewell1995BindingEnergy}
Fewell, M.~P. (1995).
``The atomic nuclide with the highest mean binding energy.''
\textit{Am. J. Phys.} \textbf{63}(7), 653--658.

\bibitem{Mossbauer1958}
M\"ossbauer, R.~L. (1958).
``Kernresonanzfluoreszenz von Gammastrahlung in Ir191.''
\textit{Z. Phys.} \textbf{151}(2), 124--143.

\bibitem{DebyeWaller1913}
Debye, P. (1913).
``Interferenz von R\"ontgenstrahlen und W\"armebewegung.''
\textit{Ann. Phys.} \textbf{348}(1), 49--92.

\bibitem{Fenton1894}
Fenton, H.~J.~H. (1894).
``Oxidation of tartaric acid in presence of iron.''
\textit{J. Chem. Soc., Trans.} \textbf{65}, 899--910.

\bibitem{Buxton1988Radiolysis}
Buxton, G.~V. et al. (1988).
``Critical review of rate constants for reactions of hydrated electrons.''
\textit{J. Phys. Chem. Ref. Data} \textbf{17}(2), 513--886.

\bibitem{Matyjaszewski1995ATRP}
Wang, J.-S. \& Matyjaszewski, K. (1995).
``Controlled/living radical polymerization. ATRP.''
\textit{J. Am. Chem. Soc.} \textbf{117}(20), 5614--5615.

\bibitem{WangMatyjaszewski2006}
Matyjaszewski, K. \& Xia, J. (2001).
``Atom transfer radical polymerization.''
\textit{Chem. Rev.} \textbf{101}(9), 2921--2990.

\bibitem{Freidberg2014Plasma}
Freidberg, J.~P. (2014).
\textit{Ideal MHD}. Cambridge University Press.

\bibitem{Putterich2010Impurity}
P\"utterich, T. et al. (2010).
``Cooling factor of tungsten.''
\textit{Nucl. Fusion} \textbf{50}(2), 025012.

\bibitem{VargaftigWater1975}
Vargaftik, N.~B. et al. (1983).
``International tables of the surface tension of water.''
\textit{J. Phys. Chem. Ref. Data} \textbf{12}(3), 817--820.

\bibitem{Leidenfrost1756}
Leidenfrost, J.~G. (1756).
\textit{De Aquae Communis Nonnullis Qualitatibus Tractatus}. Duisburg.

% === Ch.8 Golden Neighborhoods ===

\bibitem{Grothendieck1960EGA}
Grothendieck, A. \& Dieudonn\'e, J. (1960).
``\'El\'ements de g\'eom\'etrie alg\'ebrique I.''
\textit{Publ. Math. IHES} \textbf{4}, 1--228.

\bibitem{Hartshorne1977}
Hartshorne, R. (1977).
\textit{Algebraic Geometry}. Springer-Verlag, GTM~52.

\bibitem{Rota1964Umbral}
Rota, G.-C. (1964).
``The number of partitions of a set.''
\textit{Am. Math. Mon.} \textbf{71}(5), 498--504.

\bibitem{Schrodinger1944}
Schr\"odinger, E. (1944).
\textit{What is Life?} Cambridge University Press.

\bibitem{Shannon1948}
Shannon, C.~E. (1948).
``A mathematical theory of communication.''
\textit{Bell Syst. Tech. J.} \textbf{27}(3), 379--423.

% === Ch.11 Chiral Casimir Experiment ===

\bibitem{Casimir1948}
Casimir, H.~B.~G. (1948).
``On the attraction between two perfectly conducting plates.''
\textit{Proc. K. Ned. Akad. Wet.} \textbf{51}, 793--795.

\bibitem{Boyer1968}
Boyer, T.~H. (1968).
``Quantum electromagnetic zero-point energy of a conducting spherical shell.''
\textit{Phys. Rev.} \textbf{174}(5), 1764--1776.

\bibitem{Lifshitz1956}
Lifshitz, E.~M. (1956).
``The theory of molecular attractive forces between solids.''
\textit{Sov. Phys. JETP} \textbf{2}(1), 73--83.

\bibitem{Lamoreaux1997}
Lamoreaux, S.~K. (1997).
``Demonstration of the Casimir force in the 0.6 to 6 $\mu$m range.''
\textit{Phys. Rev. Lett.} \textbf{78}(1), 5--8.

\bibitem{Lv2015TaAs}
Lv, B.~Q. et al. (2015).
``Experimental discovery of Weyl semimetal TaAs.''
\textit{Phys. Rev. X} \textbf{5}(3), 031013.

% === Ch.13 Ambrosia Protocol ===

\bibitem{Berry1999Amavadin}
Berry, R.~E. et al. (1999).
``The structural characterization of amavadin.''
\textit{J. Am. Chem. Soc.} \textbf{121}(25), 5839--5840.

\bibitem{Jugdaohsingh2007Silicon}
Jugdaohsingh, R. (2007).
``Silicon and bone health.''
\textit{J. Nutr. Health Aging} \textbf{11}(2), 99--110.

\bibitem{Herraiz2004Betacarbolines}
Herraiz, T. (2004).
``Relative exposure to $\beta$-carbolines norharman and harman from foods and tobacco smoke.''
\textit{Food Addit. Contam.} \textbf{21}(11), 1041--1050.

\bibitem{Molan1992Honey}
Molan, P.~C. (1992).
``The antibacterial activity of honey.''
\textit{Bee World} \textbf{73}(1), 5--28.

\bibitem{White1963Honey}
White, J.~W., Subers, M.~H. \& Schepartz, A.~I. (1963).
``The identification of inhibine, the antibacterial factor in honey, as hydrogen peroxide.''
\textit{Biochim. Biophys. Acta} \textbf{73}, 57--70.

\bibitem{Brongersma2015LSPR}
Brongersma, M.~L., Halas, N.~J. \& Nordlander, P. (2015).
``Plasmon-induced hot carrier science and technology.''
\textit{Nat. Nanotechnol.} \textbf{10}(1), 25--34.

\bibitem{Bae2024RRT}
Bae, S., Ko, J., Song, H. \& Yun, S.-Y. (2024).
Relaxed Recursive Transformers: Effective Parameter Sharing with Layer-wise LoRA.
\textit{Proceedings of the International Conference on Learning Representations (ICLR 2025)}.
arXiv:2410.20672 [cs.CL].

\bibitem{BenderBerryMandilara2002}
Bender, C.~M., Berry, M.~V. \& Mandilara, A. (2002).
Generalized $\mathcal{PT}$ symmetry and real spectra.
\textit{Journal of Physics A: Mathematical and General}, 35(31), L467--L471.

\bibitem{BenderBrodyMuller2017}
Bender, C.~M., Brody, D.~C. \& M\"uller, M.~P. (2017).
Hamiltonian for the Zeros of the Riemann Zeta Function.
\textit{Physical Review Letters}, 118(13), 130201.

\bibitem{Chen2026DRT}
Chen, H.-H. (2026).
Thinking Deeper, Not Longer: Depth-Recurrent Transformers for Compositional Generalization.
arXiv:2603.21676 [cs.LG].

\bibitem{Conrey_RMT}
Conrey, J.~B. (2005).
Notes on $L$-functions and Random Matrix Theory.
\textit{Proceedings of Symposia in Pure Mathematics}, 73, 107--130.

\bibitem{Dehghani2019UT}
Dehghani, M., Gouws, S., Vinyals, O., Uszkoreit, J. \& Kaiser, L. (2019).
Universal Transformers.
\textit{Proceedings of the International Conference on Learning Representations (ICLR)}.
arXiv:1807.03819 [cs.CL].

\bibitem{Dirac1930}
Dirac, P. A. M. (1930).
\textit{The Principles of Quantum Mechanics}.
Oxford University Press.

\bibitem{Einstein1905}
Einstein, A. (1905).
\textit{Zur Elektrodynamik bewegter Körper} (\textit{On the Electrodynamics of Moving Bodies}).
Annalen der Physik, 322(10), 891--921.

\bibitem{Gomez2026OpenMythos}
Gomez, K. (2026).
OpenMythos: Open-Source Recurrent-Depth Transformer.
GitHub repository. \url{https://github.com/kyegomez/OpenMythos}.

\bibitem{Graves2016ACT}
Graves, A. (2016).
Adaptive Computation Time for Recurrent Neural Networks.
arXiv:1603.08983 [cs.NE].

\bibitem{Jung1969}
Jung, C. G. (1969).
\textit{The Archetypes and the Collective Unconscious} (Collected Works Vol. 9 Part 1).
Princeton University Press.

\bibitem{LVK_GWTC3}
Abbott, R. et al. (LIGO Scientific, Virgo, and KAGRA Collaborations) (2021).
\textit{GWTC-3: Compact Binary Coalescences Observed by LIGO and Virgo During the Second Part of the Third Observing Run}.
arXiv:2111.03606 [gr-qc].

\bibitem{LVK_GravitonMass}
Abbott, R. et al. (LIGO Scientific, Virgo, and KAGRA Collaborations) (2021).
\textit{Tests of General Relativity with GWTC-3} $\langle 148 \rangle$.
arXiv:2112.06861 [gr-qc].

\bibitem{Lev2010}
Lev, F.~M. (2010).
Introduction to A Quantum Theory over A Galois Field.
\textit{Symmetry}, 2(4), 1810--1845.

\bibitem{Milne2015}
Milne, J.~S. (2015).
The Riemann Hypothesis over Finite Fields: From Weil to the Present Day (a conjecture resolved for function fields by Deligne).
In \textit{The Legacy of Bernhard Riemann After One Hundred and Fifty Years}. International Press.

\bibitem{NASAExoplanet}
NASA Exoplanet Science Institute (2025).
\textit{NASA Exoplanet Archive}. California Institute of Technology.

\bibitem{NielsenChuang2010}
Nielsen, M. A., \& Chuang, I. L. (2010).
\textit{Quantum Computation and Quantum Information} (10th Anniversary ed.). Cambridge University Press.

\bibitem{Oncescu2026RT}
Oncescu, C.-A., Morwani, D., Jelassi, S., Meterez, A., Kwun, M. \& Kakade, S. (2026).
The Recurrent Transformer: Greater Effective Depth and Efficient Decoding.
arXiv:2604.21215 [cs.LG].

\bibitem{PDG2025}
Particle Data Group et al. (2025).
\textit{Review of Particle Physics (Monte Carlo Particle Numbering Scheme)}.
Phys.~Rev.~D.

\bibitem{Penrose1974}
Penrose, R. (1974).
The role of aesthetics in pure and applied mathematical research.
\textit{Bulletin of the Institute of Mathematics and its Applications}, 10, 266--271.

\bibitem{Russell1926}
Russell, W. (1926).
\textit{The Universal One: Harmonic Nuclear States and Periodic Octaves}.

\bibitem{Russell26}
Russell, W. (1926).
\textit{The Universal One}. University of Science and Philosophy.

\bibitem{TelePlasma2000}
Barrett, T.W. (2000).
\textit{NASA TelePlasma: Transforming ordinary electromagnetic fields into specially conditioned nonabelian gauge fields}.
NASA internal report / BSEI Report 1-97.

\bibitem{Frohlich1968}
Fr\"ohlich, H. (1968).
``Long-range coherence and energy storage in biological systems.''
\textit{Int. J. Quantum Chem.} \textbf{2}(5), 641--649.

\bibitem{Titius1766}
Titius, J.~D. (1766).
\textit{Translation of Charles Bonnet's Contemplation of Nature}.

\bibitem{WHIM2018}
Nicastro, F. et al. (2018).
\textit{Confirming the Detection of two WHIM Systems along the Line of Sight to 1ES 1553+113}.
arXiv:1811.03498 [astro-ph.CO].

\bibitem{aaronson2020}
S.~Aaronson,
``The Busy Beaver Frontier,''
\emph{ACM SIGACT News} 51(3), 32--54 (2020).

\bibitem{arrow1950}
K.~J.~Arrow,
``A Difficulty in the Concept of Social Welfare,''
\emph{Journal of Political Economy}, vol.~58, no.~4, pp.~328--346, 1950.

\bibitem{atasoy2017} S.~Atasoy et al., ``Connectome-harmonic decomposition of human brain activity reveals dynamical repertoire re-organization under LSD,'' \emph{Scientific Reports}\ 7, 17661 (2017).

\bibitem{atiyah-singer} Atiyah, M. F. \& Singer, I. M. (1963). The index of elliptic operators on compact manifolds. \emph{Bull.\ Amer.\ Math.\ Soc.}, 69, 422--433.

\bibitem{autoformbot} Zheng, K. et al. (2026). AutoformBot: Multi-agent textbook formalization at scale. \emph{arXiv:2605.14332}.

\bibitem{baez-octonions} Baez, J. C. (2002). The Octonions. \emph{Bull.\ Amer.\ Math.\ Soc.}, 39(2), 145--205.

\bibitem{bahamonde2023}
S.~Bahamonde et al., ``Teleparallel Gravity: From Theory to Cosmology,'' \emph{Rep. Prog. Phys.} \textbf{86}, 026901, 2023.

\bibitem{bender-berry-mandilara}
Bender, C.~M., Berry, M.~V. \& Mandilara, A. (2002).
Generalized $\mathcal{PT}$ symmetry and real spectra.
\emph{Journal of Physics A: Mathematical and General}, 35(31), L467--L471.

\bibitem{bender-berry-mandilara-12} C.~M.~Bender, M.~V.~Berry, and A.~Mandilara, ``Generalized $\mathcal{PT}$ symmetry and real spectra,'' \emph{J.\ Phys.\ A}\ 35(31), L467--L471 (2002).

\bibitem{bender-brody-muller}
Bender, C.~M., Brody, D.~C. \& M\"uller, M.~P. (2017).
Hamiltonian for the Zeros of the Riemann Zeta Function.
\emph{Physical Review Letters}, 118(13), 130201.

\bibitem{bender-brody-muller-12} C.~M.~Bender, D.~C.~Brody, and M.~P.~M\"uller, ``Hamiltonian for the Zeros of the Riemann Zeta Function,'' \emph{Physical Review Letters}\ 118(13), 130201 (2017).

\bibitem{black_scholes1973}
F.~Black and M.~Scholes,
``The Pricing of Options and Corporate Liabilities,''
\emph{Journal of Political Economy}, vol.~81, no.~3, pp.~637--654, 1973.

\bibitem{blagg1913} M.~A.~Blagg, ``On a suggested substitute for Bode's Law,'' \emph{MNRAS}\ 73, 414--422 (1913).

\bibitem{bohm} Bohm, D. (1980). \emph{Wholeness and the Implicate Order}. Routledge.

\bibitem{borcherds} Borcherds, R. E. (1992). Monstrous moonshine and monstrous Lie superalgebras. \emph{Inventiones Mathematicae}, 109(1), 405--444.

\bibitem{bostrom-surreal} Bostrom, N. (2011). Infinite Ethics. \emph{Analysis and Metaphysics}, 10, 9--59.

\bibitem{bovaird2013} T.~Bovaird and C.~H.~Lineweaver, ``Exoplanet predictions based on the generalized Titius-Bode relation,'' \emph{MNRAS}\ 435, 1126--1138 (2013).

\bibitem{boyer1968}
T.~H.~Boyer,
``Quantum Electromagnetic Zero-Point Energy of a Conducting Spherical Shell and the Casimir Model for a Charged Particle,''
\emph{Physical Review}, vol.~174, pp.~1764--1776, 1968.

\bibitem{buzzard-xena} Buzzard, K. (2020). Formalising Mathematics in Lean. \emph{Notices of the AMS}, 67(11), 1613--1618.

\bibitem{calaque-ronchi} Calaque, D. and Ronchi, S. (2026). Shifted Symplectic Geometry by Examples. arXiv:2510.04625v3.

\bibitem{calude-randomness} Calude, C. S. \& J\"urgensen, H. (2005). Is complexity a source of incompleteness? \emph{Advances in Applied Mathematics}, 35(1), 1--15.

\bibitem{carhart2019} R.~L.~Carhart-Harris and K.~J.~Friston, ``REBUS and the Anarchic Brain: Toward a Unified Model of the Brain Action of Psychedelics,'' \emph{Pharmacol Rev}\ 71(3), 316-344 (2019).

\bibitem{casimir1948}
H.~B.~G.~Casimir,
``On the Attraction Between Two Perfectly Conducting Plates,''
\emph{Proc. Kon. Ned. Akad. Wetensch.}, vol.~51, pp.~793--795, 1948.

\bibitem{chaitin-omega} Chaitin, G. J. (1975). A theory of program size formally identical to information theory. \emph{J.\ ACM}, 22(3), 329--340.

\bibitem{chevalley1936} Chevalley, C. (1936). La th\'eorie du symbole de restes normiques. \emph{Journal f\"ur die reine und angewandte Mathematik}, 1936(176), 73--94.

\bibitem{comsoc2016}
F.~Brandt, V.~Conitzer, U.~Endriss, J.~Lang, and A.~D.~Procaccia, eds.,
\emph{Handbook of Computational Social Choice},
Cambridge University Press, 2016.

\bibitem{connes} Connes, A. (1994). \emph{Noncommutative Geometry}. Academic Press.

\bibitem{connes-consani-zeta} Connes, A., Consani, C., \& Moscovici, H. (2023). Zeta zeros and prolate wave operators. \emph{arXiv:2310.18223}.

\bibitem{connes-consani2014}
A.~Connes and C.~Consani,
``The Arithmetic Site,''
\emph{Comptes Rendus Math\'ematique} 352(12), 971--975 (2014).

\bibitem{connes-marcolli} Connes, A. \& Marcolli, M. (2008). \emph{Noncommutative Geometry, Quantum Fields and Motives}. AMS.

\bibitem{connes-scaling} Connes, A. \& Consani, C. (2021). Weil positivity and trace formula. \emph{arXiv:2112.07565}.

\bibitem{conrey-rmt}
Conrey, J.~B. (2005).
Notes on $L$-functions and Random Matrix Theory.
\emph{Proceedings of Symposia in Pure Mathematics}, 73, 107--130.

\bibitem{conrey-rmt-12} J.~B.~Conrey, ``Notes on $L$-functions and Random Matrix Theory,'' \emph{Proc.\ Sympos.\ Pure Math.}\ 73, 107--130 (2005).

\bibitem{conway} Conway, J. H. (1976). \emph{On Numbers and Games}. Academic Press.

\bibitem{conway-norton} Conway, J. H. \& Norton, S. P. (1979). Monstrous Moonshine. \emph{Bull.\ London Math.\ Soc.}, 11(3), 308--339.

\bibitem{coppersmith1994}
D.~Coppersmith,
``An approximate Fourier transform,''
IBM Research Report RC19642 (1994).

\bibitem{creutz1980}
M.~Creutz,
``Monte Carlo study of quantized SU(2) gauge theory,''
\emph{Phys. Rev. D}\ 21, 2308--2315 (1980).

\bibitem{curry-howard} Howard, W. A. (1980). The formulae-as-types notion of construction. In \emph{To H.B. Curry: Essays on Combinatory Logic}, pp.~479--490.

\bibitem{damour1979}
T.~Damour, ``The Problem of Motion in Newtonian and Einsteinian Gravity,'' in \emph{Three Hundred Years of Gravitation}, eds. S.~Hawking and W.~Israel, Cambridge Univ. Press, 1987.

\bibitem{deShalit2016}
de~Shalit, E. (2016).
Mahler bases and elementary $p$-adic analysis.
\textit{Journal de Th\'eorie des Nombres de Bordeaux}, 28(3), 597--620.

\bibitem{demoura-lean4} de Moura, L. \& Ullrich, S. (2021). The Lean Theorem Prover and Programming Language. In \emph{CADE-28}, LNCS 12699, pp.~625--635.

\bibitem{derham} de Rham, G. (1931). Sur l'analysis situs des vari\'et\'es \`a $n$ dimensions. \emph{J.\ Math.\ Pures Appl.}, 10, 115--200.

\bibitem{dermott1968} S.~F.~Dermott, ``On the origin of commensurabilities in the solar system---II,'' \emph{MNRAS}\ 141, 363--376 (1968).

\bibitem{deshalit-mahler}
de~Shalit, E. (2016).
Mahler bases and elementary $p$-adic analysis.
\emph{Journal de Th\'eorie des Nombres de Bordeaux}, 28(3), 597--620.

\bibitem{deshalit-mahler-12} E.~de~Shalit, ``Mahler bases and elementary $p$-adic analysis,'' \emph{J.\ Th\'eorie des Nombres de Bordeaux}\ 28(3), 597--620 (2016).

\bibitem{diep_frustrated}
H.~T.~Diep, ed.,
\emph{Frustrated Spin Systems},
2nd ed., World Scientific, 2013.

\bibitem{dirac} Dirac, P. A. M. (1930). \emph{The Principles of Quantum Mechanics}. Oxford University Press.

\bibitem{eckerli2021}
F.~Eckerli and J.~Osterrieder,
``Generative Adversarial Networks in Finance: An Overview,''
\emph{arXiv:2106.06364}, 2021.

\bibitem{eichenauer1986non}
J. Eichenauer and J. Lehn,
\textit{A Non-Linear Congruential Pseudo Random Number Generator},
Statistische Hefte, 27(1):315--326, 1986.

\bibitem{eichten1980}
E.~Eichten, K.~Gottfried, T.~Kinoshita, K.~Lane, and T.-M.~Yan, ``Charmonium: Comparison with Experiment,'' \emph{Phys. Rev. D} \textbf{21}, 203, 1980.

\bibitem{Elser85}
V.~Elser and C.~L.~Henley,
``Crystal and quasicrystal structures in Al--Mn alloys,''
\emph{Phys.~Rev.~Lett.} \textbf{55}, 2883--2886 (1985).

\bibitem{euler-identity} Euler, L. (1748). \emph{Introductio in Analysin Infinitorum}. Lausanne.

\bibitem{fernstrom71} J.~D.~Fernstrom and R.~J.~Wurtman, ``Brain serotonin content: physiological regulation by plasma neutral amino acids,'' \emph{Science}\ 173, 149 (1971).

\bibitem{feynman} Feynman, R. P., Leighton, R. B., \& Sands, M. (1964). \emph{The Feynman Lectures on Physics}. Addison-Wesley.

\bibitem{feynman_qcd}
R.~P.~Feynman, ``The behavior of hadron collisions at extreme energies,'' in \emph{High Energy Collisions: Third International Conference}, Gordon and Breach, 1969.

\bibitem{fibonacci} Fibonacci (Leonardo of Pisa). (1202). \emph{Liber Abaci}. Translated by L.\,E.\ Sigler (2002), Springer.

\bibitem{fingan2024}
Man AHL Research,
``Fin-GAN: Forecasting and Simulating Financial Time Series with Generative Adversarial Networks,''
\emph{Man Group Research Papers}, 2024.

\bibitem{fractalEEG} S.~Buzs\'aki and K.~Mizuseki, ``The log-dynamic brain: how skewed distributions affect network operations,'' \emph{Nature Reviews Neuroscience}\ 15, 264-278 (2014).

\bibitem{fractalPathology} E.~Bullmore et al., ``Fractal analysis of the electroencephalogram in depression and schizophrenia,'' \emph{IEEE Trans Biomed Eng}\ (1994).

\bibitem{Friedel88}
J.~Friedel,
``Do Hume-Rothery rules still hold? Old and new electron phases in metallic alloys,''
\emph{Phil.~Mag.~B} \textbf{58}(4), 413--427 (1988).

\bibitem{gabor1946}
D.~Gabor,
``Theory of Communication,''
\emph{Journal of the Institution of Electrical Engineers}, vol.~93, no.~26, pp.~429--457, 1946.

\bibitem{gellmann}
M.~Gell-Mann, ``A schematic model of baryons and mesons,'' \emph{Physics Letters}, vol.~8, no.~3, pp.~214--215, 1964.

\bibitem{gibbard1973}
A.~Gibbard,
``Manipulation of Voting Schemes: A General Result,''
\emph{Econometrica}, vol.~41, no.~4, pp.~587--601, 1973.

\bibitem{godel} G\"odel, K. (1931). \"Uber formal unentscheidbare S\"atze der Principia Mathematica und verwandter Systeme~I. \emph{Monatshefte f\"ur Mathematik und Physik}, 38, 173--198.

\bibitem{goodstein} Goodstein, R. L. (1944). On the restricted ordinal theorem. \emph{J.\ Symbolic Logic}, 9(2), 33--41.

\bibitem{goodstein1947}
R.~L.~Goodstein,
``Transfinite Ordinals in Recursive Number Theory,''
\emph{Journal of Symbolic Logic} 12(4), 123--129 (1947).

\bibitem{graner1994} F.~Graner and B.~Dubrulle, ``Titius-Bode laws in the solar system. I. Scale invariance explains everything,'' \emph{Astron. Astrophys.}\ 282, 262--268 (1994).

\bibitem{greensite}
J.~Greensite, \emph{An Introduction to the Confinement Problem}, 2nd ed., Lecture Notes in Physics, vol.~972, Springer, 2020. (Center symmetry and $Z(N)$ vortex confinement: Ch.~4--5.)

\bibitem{grothendieck} Grothendieck, A. (1984). \emph{Esquisse d'un Programme}.

\bibitem{grothendieck-rs} Grothendieck, A. (1985--1986). \emph{R\'ecoltes et Semailles: R\'eflexions et T\'emoignage sur un Pass\'e de Math\'ematicien}. Universit\'e des Sciences et Techniques du Languedoc, Montpellier.

\bibitem{grothendieck_ega}
A.~Grothendieck and J.~Dieudonn\'e,
``\'El\'ements de g\'eom\'etrie alg\'ebrique,''
\emph{Inst. Hautes \'Etudes Sci. Publ. Math.}, 1960--1967.

\bibitem{gutin} Gutin, R. (2020). Constructive proof of Herschfeld's Convergence Theorem. \emph{Mathematics of Computation}, 89, 237--251.

\bibitem{hameroff2014} S.~Hameroff and R.~Penrose, ``Consciousness in the universe: A review of the `Orch OR' theory,'' \emph{Physics of Life Reviews}\ 11(1), 39--78 (2014).

\bibitem{hatcher} Hatcher, A. (2002). \emph{Algebraic Topology}. Cambridge University Press.

\bibitem{hod1998}
S.~Hod (1998).
``Bohr's correspondence principle and the area spectrum of quantum black holes.''
\textit{Phys.\ Rev.\ Lett.} 81, 4293.

\bibitem{hopfield} Hopfield, J. J. (1982). Neural networks and physical systems with emergent collective computational abilities. \emph{Proc.\ Natl.\ Acad.\ Sci.}, 79(8), 2554--2558.

\bibitem{hull2018}
J.~C.~Hull,
\emph{Options, Futures, and Other Derivatives},
10th ed., Pearson, 2018.

\bibitem{ilinski1997}
K.~Ilinski,
``Physics of Finance,''
\emph{arXiv:hep-th/9710148}, 1997.

\bibitem{jaffe2000}
A.~Jaffe and E.~Witten,
``Quantum Yang-Mills Theory,''
Official Problem Description, Clay Mathematics Institute (2000).

\bibitem{jaramillo} Jaramillo Salazar, J. D. (2020). Hyperoperations in Exponential Fields. \emph{Journal of Algebra and Its Applications}, 19(1).

\bibitem{jiang_wilczek2019}
Q.-D.~Jiang and F.~Wilczek,
``Chiral Casimir forces: Repulsive, enhanced, tunable,''
\emph{Physical Review B}, vol.~99, no.~12, p.~125403, 2019.

\bibitem{katrin}
M.~Aker \emph{et al.} (KATRIN Collaboration), ``Direct neutrino-mass measurement with sub-electronvolt sensitivity,'' \emph{Nature Physics}, vol.~18, pp.~160--166, 2022.

\bibitem{kerodon} Lurie, J. (2018--). \emph{Kerodon}. \url{https://kerodon.net}.

\bibitem{kim2001}
J.~Kim, ``Neutrino Mass and Mixing,'' \emph{Phys. Rep.} \textbf{150}, 1--177, 2001.

\bibitem{knuth-surreal} Knuth, D. E. (1974). \emph{Surreal Numbers}. Addison-Wesley.

\bibitem{knuth1976}
D.~E.~Knuth,
``Mathematics and Computer Science: Coping with Finiteness,''
\emph{Science} 194(4271), 1235--1242 (1976).
Introduces the up-arrow notation for Goodstein's hyperoperation hierarchy.

\bibitem{kolmogorov1941}
A.~N.~Kolmogorov,
``The local structure of turbulence in incompressible viscous fluid for very large Reynolds numbers,''
\emph{Doklady Akademii Nauk SSSR}, vol.~30, pp.~299--303, 1941.

\bibitem{konkoly2021} K.~R.~Konkoly et al., ``Real-time dialogue between experimenters and dreamers during REM sleep,'' \emph{Current Biology}\ 31(7), 1417-1427.e6 (2021).

\bibitem{krapivin2025optimal}
M.~Farach-Colton, A.~Krapivin, and W.~Kuszmaul,
``Optimal Bounds for Open Addressing Without Reordering,''
arXiv preprint arXiv:2501.02305 (2025).

\bibitem{landauer} Landauer, R. (1961). Irreversibility and Heat Generation in the Computing Process. \emph{IBM Journal of Research and Development}, 5(3), 183--191.

\bibitem{layden2025}
D.~Layden et al., ``Quantum Error Correction Below the Surface Code Threshold,'' \emph{Nature} \textbf{638}, 2025.

\bibitem{lemouël2025}
J.-L.~Le Mou\"{e}l, V.~Courtillot, and S.~Gibert, ``SolDynamo: Solar Dynamo and Planetary Coupling,'' preprint, 2025.

\bibitem{lev-finite-math}
Lev, F.~M. (2020).
Finite Mathematics as the Foundation of Classical Mathematics and Quantum Theory.
Springer.

\bibitem{lev-gfqt}
Lev, F.~M. (2010).
Introduction to A Quantum Theory over A Galois Field.
\emph{Symmetry}, 2(4), 1810--1845.

\bibitem{lev-gfqt-3}
F.~M.~Lev,
``Introduction to A Quantum Theory over A Galois Field,''
\emph{Symmetry} 2(4), 1810--1845 (2010).

\bibitem{lockwood} Lockwood, J. (2024). Chronometric Coordination in Distributed Temporal Systems. \emph{Journal of Distributed Computing}, 37(4), 215--234.

\bibitem{lockwood_zpe2025}
J.~Lockwood,
``Fractal Spacetime and Zero-Point Energy,'' 2025.

\bibitem{lopezdeprado2018}
M.~L\'{o}pez de Prado,
\emph{Advances in Financial Machine Learning},
Wiley, 2018.
Chapter 11: ``The Dangers of Backtesting.'' Sustained precision above 50\% on crash classification tasks invites scrutiny for look-ahead bias and data leakage.

\bibitem{luminet2003}
J.-P.~Luminet, J.~R.~Weeks, A.~Riazuelo, R.~Lehoucq, J.-P.~Uzan (2003).
``Dodecahedral space topology as an explanation for weak wide-angle temperature correlations in the cosmic microwave background.''
\textit{Nature} 425, 593--595.

\bibitem{lurie-htt} Lurie, J. (2009). \emph{Higher Topos Theory}. Princeton University Press.

\bibitem{maclane-moerdijk} Mac Lane, S. \& Moerdijk, I. (1992). \emph{Sheaves in Geometry and Logic}. Springer-Verlag.

\bibitem{malcev} Mal'cev, A. I. (1955). Analytic loops. \emph{Mat.\ Sb.}, 36(78), 569--576.

\bibitem{maluf2013}
J.~Maluf, ``The Teleparallel Equivalent of General Relativity,'' \emph{Annalen der Physik} \textbf{525}, 339--357, 2013.

\bibitem{mandelbrot} Mandelbrot, B. B. (1982). \emph{The Fractal Geometry of Nature}. W.\,H.\ Freeman.

\bibitem{mandelbrot1963}
B.~B.~Mandelbrot,
``The Variation of Certain Speculative Prices,''
\emph{The Journal of Business}, vol.~36, no.~4, pp.~394--419, 1963.

\bibitem{manton2002}
N.~S.~Manton,
``Fluid mechanical models of financial markets,''
Working paper, DAMTP Cambridge, 2002.

\bibitem{massot-blueprints} Massot, P. (2023). Lean Blueprints: Bridging Informal and Formal Mathematics. In \emph{ITP 2023}, LIPIcs.

\bibitem{mathlib} The mathlib Community. (2020). The Lean Mathematical Library. In \emph{CPP '20}, pp.~367--381. ACM.

\bibitem{may-ponto} May, J. P. \& Ponto, K. (2012). \emph{More Concise Algebraic Topology}. University of Chicago Press.

\bibitem{mckinney05} J.~McKinney et al., ``A revised mechanism for tryptophan hydroxylase,'' \emph{J.~Biol.~Chem.}\ 280, 13265 (2005).

\bibitem{milne-rhff}
Milne, J.~S. (2015).
The Riemann Hypothesis over Finite Fields: From Weil to the Present Day (a conjecture resolved for function fields by Deligne).
In \emph{The Legacy of Bernhard Riemann After One Hundred and Fifty Years}. International Press.

\bibitem{milne-rhff-12} J.~S.~Milne, ``The Riemann Hypothesis over Finite Fields,'' in \emph{The Legacy of Bernhard Riemann After One Hundred and Fifty Years}, International Press (2015).

\bibitem{milne-rhff-3}
J.~S.~Milne,
``The Riemann Hypothesis over Finite Fields: From Weil to the Present Day,''
in \emph{The Legacy of Bernhard Riemann After One Hundred and Fifty Years},
International Press (2015).

\bibitem{milne_cft}
J.~S.~Milne,
``Class Field Theory,''
lecture notes, v4.03, 2020.

\bibitem{milnor} Milnor, J. (1963). \emph{Morse Theory}. Princeton University Press.

\bibitem{montgomery} Montgomery, H. L. (1973). The pair correlation of zeros of the zeta function. \emph{Analytic Number Theory}, 181--193.

\bibitem{motl2003}
L.~Motl and A.~Neitzke (2003).
``Asymptotic black hole quasinormal frequencies.''
\textit{Adv.\ Theor.\ Math.\ Phys.} 7, 307--330.

\bibitem{mrs_glutamate} R.~A.~E.~Edden et al., ``Proton MR spectroscopy of GABA, glutamate, and glutamine,'' \emph{Neuroimage}, 2012.

\bibitem{mrs_variance} A.~Bogaschewsky et al., ``Reproducibility of Glx and GABA measurements in the human brain,'' \emph{Magnetic Resonance in Medicine}, 2019.

\bibitem{nagatsu64} T.~Nagatsu, M.~Levitt, and S.~Udenfriend, ``Tyrosine Hydroxylase: The Initial Step in Norepinephrine Biosynthesis,'' \emph{J Biol Chem}\ 239, 2910--2917 (1964).

\bibitem{nash} Nash, J. F. (1950). Equilibrium points in $n$-person games. \emph{Proc.\ Natl.\ Acad.\ Sci.}, 36(1), 48--49.

\bibitem{neukirch}
J.~Neukirch,
\emph{Algebraic Number Theory},
Grundlehren der mathematischen Wissenschaften, vol.~322, Springer, 1999.

\bibitem{newton}
I.~Newton, \emph{Opticks: or, A Treatise of the Reflexions, Refractions, Inflexions and Colours of Light}, 1704.

\bibitem{odlyzko} Odlyzko, A. M. (1987). On the distribution of spacings between zeros of the zeta function. \emph{Mathematics of Computation}, 48(177), 273--308.

\bibitem{odrzywolek} Odrzywolek, A. (2026). All elementary functions from a single operator. \emph{arXiv preprint}.

\bibitem{padicCognition} A.~Khrennikov, \emph{Information Dynamics in Cognitive, Psychological, Social and Anomalous Phenomena}, Springer (2004).

\bibitem{penrose} Penrose, R. (1989). \emph{The Emperor's New Mind}. Oxford University Press.

\bibitem{penrose-qp} Penrose, R. (1974). The role of aesthetics in pure and applied mathematical research. \emph{Bull.\ IMA}, 10(7/8), 266--271.

\bibitem{perlin1985image}
Ken Perlin,
\textit{An Image Synthesizer},
SIGGRAPH Computer Graphics, 19(3):287--296, 1985.

\bibitem{persson_minecraft}
M. Persson et al.,
\textit{Minecraft: Deterministic Voxel Generation and LCGs},
Mojang Specifications (Informal Technical Documentation), 2009--2011.

\bibitem{pitkanenTGD} M.~Pitk\"anen, ``TGD Inspired Theory of Consciousness,'' \emph{Journal of Non-Locality and Remote Mental Interactions}\ 1 (2002).

\bibitem{planck2020}
Planck Collaboration (2020).
``Planck 2018 results.\ VII.\ Isotropy and statistics of the CMB.''
\textit{Astron.\ Astrophys.} 641, A7.

\bibitem{pollard1971}
J.~M.~Pollard,
``The fast Fourier transform in a finite field,''
\emph{Math.\ Comp.} 25(114), 365--374 (1971).

\bibitem{ptvv} Pantev, T., To\"en, B., Vaqui\'e, M. and Vezzosi, G. (2013). Shifted symplectic structures. \emph{Publ. Math. Inst. Hautes \'Etudes Sci.} 117, 271--328.

\bibitem{rado1962}
T.~Rad\'o,
``On Non-Computable Functions,''
\emph{Bell System Technical Journal} 41(3), 877--884 (1962).

\bibitem{riemann} Riemann, B. (1859). Ueber die Anzahl der Primzahlen unter einer gegebenen Gr\"osse. \emph{Monatsberichte der Berliner Akademie}.

\bibitem{robinson} Robinson, A. (1966). \emph{Non-standard Analysis}. North-Holland.

\bibitem{roy1954} A.~E.~Roy and M.~W.~Ovenden, ``On the occurrence of commensurable mean motions in the solar system,'' \emph{MNRAS}\ 114, 232--241 (1954).

\bibitem{safe-verification} Xin, H. et al. (2025). Safe: Step-aware formal verification for LLM reasoning. \emph{Proc.\ ACL}, pp.~4821--4838.

\bibitem{satterthwaite1975}
M.~A.~Satterthwaite,
``Strategy-Proofness and Arrow's Conditions,''
\emph{Journal of Economic Theory}, vol.~10, no.~2, pp.~187--217, 1975.

\bibitem{savitz20} J.~Savitz, ``The kynurenine pathway: a finger in every pie,'' \emph{Mol Psychiatry}\ 25, 131--147 (2020).

\bibitem{schafer} Schafer, R. D. (1966). \emph{An Introduction to Nonassociative Algebras}. Academic Press.

\bibitem{schrodinger}
E.~Schr\"odinger, ``Quantisierung als Eigenwertproblem,'' \emph{Annalen der Physik}, vol.~384, no.~4, pp.~361--376, 1926.

\bibitem{schrodinger44}
E.~Schr\"odinger,
\emph{What is Life? The Physical Aspect of the Living Cell},
Cambridge University Press, 1944.
Chapter~6: ``Order, Disorder, and Entropy.''

\bibitem{schwieler16} L.~Schwieler et al., ``Electroconvulsive therapy suppresses the neurotoxic branch of the kynurenine pathway in treatment-resistant depressed patients,'' \emph{Transl Psychiatry}\ 6, e906 (2016).

\bibitem{serre_local}
J.-P.~Serre,
\emph{Local Fields},
Graduate Texts in Mathematics, vol.~67, Springer, 1979.

\bibitem{shannon} Shannon, C. E. (1948). A mathematical theory of communication. \emph{Bell System Technical Journal}, 27(3), 379--423.

\bibitem{shannon48}
C.~E.~Shannon,
``A Mathematical Theory of Communication,''
\emph{Bell System Technical Journal} 27, 379--423, 623--656 (1948).

\bibitem{shor1994}
P.~W.~Shor,
``Algorithms for quantum computation: discrete logarithms and factoring,''
\emph{Proceedings 35th Annual Symposium on Foundations of Computer Science}, IEEE, 124--134 (1994).

\bibitem{shulgin_pihkal}
A.~T.~Shulgin and A.~Shulgin,
\emph{PiHKAL: A Chemical Love Story},
Transform Press, 1991.

\bibitem{sono96} M.~Sono et al., ``Heme-containing oxygenases,'' \emph{Chem.\ Rev.}\ 96, 2841 (1996).

\bibitem{srinivasan15} B.~Srinivasan et al., ``TEER measurement techniques for in vitro barrier model systems,'' \emph{JALA}\ 20, 107 (2015).

\bibitem{steenrod} Steenrod, N. (1951). \emph{The Topology of Fibre Bundles}. Princeton University Press.

\bibitem{stillinger1977}
F.~Stillinger, ``Axiomatic Basis for Spaces with Noninteger Dimension,'' \emph{J. Math. Phys.} \textbf{18}, 1224--1234, 1977.

\bibitem{stockigt11} J.~St\"ockigt et al., ``The Pictet--Spengler reaction in nature and in organic chemistry,'' \emph{Angew.~Chem.}\ 50, 7580 (2011).

\bibitem{takahashi2019}
S.~Takahashi, Y.~Chen, and K.~Tanaka-Ishii,
``Modeling Financial Time-Series with Generative Adversarial Networks,''
\emph{Physica A: Statistical Mechanics and its Applications}, vol.~527, 121261, 2019.

\bibitem{tarski} Tarski, A. (1936). Der Wahrheitsbegriff in den formalisierten Sprachen. \emph{Studia Philosophica}, 1, 261--405.

\bibitem{thooft1981}
G.~'t~Hooft,
``Topology of the gauge condition and new confinement phases in non-Abelian gauge theories,''
\emph{Nucl. Phys. B}\ 190, 455--478 (1981).

\bibitem{timegan2019}
J.~Yoon, D.~Jarrett, and M.~van der Schaar,
``Time-series Generative Adversarial Networks,''
\emph{Advances in Neural Information Processing Systems (NeurIPS)}, 2019.

\bibitem{tsai-spaceq} Eby, J., Safronova, M. S., \& Tsai, Y.-D. (2022). Direct detection of ultralight dark matter bound to the Sun with space quantum sensors. \emph{Nature Astronomy}, 6, 1233--1239.

\bibitem{ttsgan2024}
X.~Li, V.~Metsis, H.~Wang, and A.~Ngu,
``TTS-GAN: A Transformer-based Time-Series Generative Adversarial Network,''
\emph{arXiv:2202.02691v3}, 2024.

\bibitem{varieschi2020}
G.~Varieschi, ``Newtonian Fractional-Dimension Gravity and MOND,'' \emph{Found. Phys.} \textbf{50}, 1608--1644, 2020.

\bibitem{veblen} Veblen, O. (1908). Continuous Increasing Functions of Finite and Transfinite Ordinals. \emph{Trans.\ AMS}, 9(3), 280--292.

\bibitem{wiener} Wiener, N. (1948). \emph{Cybernetics: Or Control and Communication in the Animal and the Machine}. MIT Press.

\bibitem{wilczek1973}
F.~Wilczek, ``Ultraviolet Stability of the Vacuum in a Non-Abelian Gauge Theory,'' \emph{Phys. Rev. Lett.} \textbf{30}, 1343--1346, 1973.

\bibitem{wilson1974}
K.~G.~Wilson,
``Confinement of quarks,''
\emph{Phys. Rev. D}\ 10, 2445--2459 (1974).


% ────────────────────────────────────────────
% AUTHOR'S WORKS, PREPRINTS, AND
% PRIVATE COMMUNICATIONS
% ────────────────────────────────────────────
% Works by the author(s) of this volume,
% preprints not yet peer-reviewed, private
% communications, and informal sources.
% These have NOT undergone external peer review.
% ────────────────────────────────────────────

\bibitem{Aingel}
La Rue, D. (2026).
\texttt{Aingel\_proofs}: The ZKP Holochain Envelope over the Metareal Manifold.
Formal algebraic synthesis.

\bibitem{GoldenTetrahedron}
La Rue, D. (2026).
\textit{The Golden Tetrahedron: Gauge Center Hierarchy and Chronometric Structure}.

\bibitem{InfochemicalTime}
La Rue, D. (2026).
\texttt{InfochemicalTime\_proofs}: Quasi-Epi-Periodic Geometric Time.
Formal algebraic synthesis.

\bibitem{MetarealManifold}
La Rue, D. (2026).
\texttt{MetarealManifold\_proofs}: The 12-Dimensional Observer-Manifold Space.
Formal algebraic synthesis.

\bibitem{PrimeFieldMechanics}
La Rue, D. (2026).
\texttt{PrimeFieldMechanics\_proofs}: Agentic Mechanics.
Formal algebraic synthesis.

\bibitem{bionetic_ambrosia}
D.~La Rue,
``The Bionetic Ambrosia Protocol,''
June 2026.

\bibitem{btc_indicator2025}
Various,
``Bitcoin as a Leading Indicator for Risk Appetite: 24/7 Liquidity Signals and Equity Market Correlation,''
Market microstructure research and institutional reports, 2024--2026.

\bibitem{crashbenchmark2024}
Various,
``Stock Market Crash Prediction: Evaluation Metrics and Model Comparison,''
Academic surveys across machine learning and econometric approaches, 2020--2024.
Typical precision for 3-month crash prediction: $\sim$15\% at recall $\sim$59\%.

\bibitem{dwm}
D.~La Rue,
``Digital Wave Mechanics,'' 2025.

\bibitem{dwm_fst}
J.~Lockwood and D.~La Rue, ``Digital Wave Mechanics and Fractal Spacetime: Adelic Orbit Structure of the Chronometric Triangle,'' preprint, June 2026.

\bibitem{ewsbenchmark2024}
Various,
``Machine Learning Early Warning Systems for Financial Crises,''
Studies from Bank of Canada, ECB, IMF, and academic papers, 2020--2026.
State-of-the-art AUROC: 0.75--0.88 for 6-month recession forecasting using 15--50 macroeconomic indicators.

\bibitem{gans_diffusion2024}
Various,
``GAN-Guided Diffusion Models for Financial Time Series,''
\emph{arXiv preprints}, 2024--2025.

\bibitem{golden_tetrahedron}
D.~La Rue,
``The Golden Tetrahedron: Algebraic Foundations of Standard Model Symmetries,''
2026.

\bibitem{hci_prompt2025}
Various,
``Human-Computer Interaction in Financial Trading Systems: Market Research and Design Principles,''
Industry reports and academic surveys, 2025--2026.

\bibitem{larue} La Rue, D. (2026). Protoreal Zeta. Formal verification of topological and algebraic axioms. \url{https://github.com/Dielawn-01/ProtorealZeta}.

\bibitem{larue-cde} La Rue, D. \& Lockwood, J. (2026). SU(3) Center Drift Extension: Golden Cosets and Temporal Spectral Dynamics.

\bibitem{larue2026chromatic}
D.~La Rue.
\textit{The SU(3) Center Triangle and Fractal SpaceTime} (Digital Wave Mechanics).
Spectrality Institute, 2026.

\bibitem{larue2026lc}
D. La Rue.
\textit{Logical Creativity and the La Rue Manifold}.
Spectrality Institute, 2026.

\bibitem{larue_chromatic}
D.~La Rue, ``The SU(3) Center Triangle: Golden Split Primes, Standing Waves in Digit Space, and the Dark-Bright Palindrome Resonance,'' preprint, June 2026.

\bibitem{larue_dwm}
D.~La Rue and J.~Lockwood,
``Digital Wave Mechanics and Fractal Spacetime,''
Preprint, June 2026.

\bibitem{larue_lc}
D.~La Rue, ``Logical Creativity: A Discussion on the Foundations of Mathematics,'' preprint, June 2026.

\bibitem{lc} D.~La Rue, \emph{Logical Creativity}, Protoreal Zeta Series, 2026.

\bibitem{lockwood2025dwm}
D.~La Rue and J.~Lockwood.
\textit{Digital Wave Mechanics}.
Spectrality Institute, 2025.

\bibitem{lockwood2025zpe}
J.~Lockwood.
\textit{Zero-Point Energy: First Principles, Units, and Observables}.
Spectrality Institute, Sept 2025.

\bibitem{lockwood_chrono}
J.~Lockwood,
``Chronometric Constants and Frozen Spectral Relations,''
Private communication, 2026.

\bibitem{lockwood_chrono3}
J.~Lockwood, ``Chronometric Constants and Frozen Spectral Relations (Chrono~3),'' private communication, 2026.

\bibitem{lockwood_chrono4}
J.~Lockwood, ``Chronometric Constants and Frozen Spectral Relations (Chrono~4),'' private communication, 2026.

\bibitem{lockwood_larue_dwm}
J.~Lockwood and D.~La Rue,
``Digital Wave Mechanics: From Newton's Prism to Standing Waves
in Finite Golden Fields,'' 2026.

\bibitem{lockwood_v11}
M.~Lockwood, ``Solar Cycle Prediction: v11 Update,'' private communication, 2025.

\bibitem{metareal_asi}
D.~La Rue,
``Metareal ASI Chromodynamics: The Golden Veblen Resolution of G\"odelian Incompleteness,''
June 2026.

\bibitem{plasma} D.~La Rue, \emph{InfoPhys Lattice Dynamics}, Metamaterial Research Export, 2026. \url{https://github.com/Dielawn-01/InfoPhys}

\bibitem{protoreal} D.~La Rue, \emph{Protoreal Zeta}, formal axioms, 2026. \url{https://github.com/Dielawn-01/Protoreal_Zeta}

\bibitem{rj2} J.~Lockwood and D.~Hansley, \emph{Royal Jelly: Field--Transport Foundations for Bioelectromagnetics}, Spectrality Institute, 2025.

\bibitem{rja} D.~La Rue, \emph{Transport--Algebraic Correspondence in Bioelectromagnetics: An Analysis of the Royal Jelly Framework}, InfoPhys Axioms, 2026.

\bibitem{steiniger2026epg}
Steiniger, R.,
``Engineering Persistent Geometric Identities in LLMs,''
Preprint v3, May 2026.

\bibitem{walker_infoton}
M.~Walker, ``The Infoton, the Blackbody Constant of Information-Energy, and the
Landauer Wall,'' private communication, 2024.

% ═══ Time Crystals ═══════════════════════════════════
\bibitem{wilczek2012}
F.~Wilczek,
``Quantum Time Crystals,''
\emph{Physical Review Letters}, vol.~109, 160401, 2012.

\bibitem{watanabe2015}
H.~Watanabe and M.~Oshikawa,
``Absence of Quantum Time Crystals,''
\emph{Physical Review Letters}, vol.~114, 251603, 2015.

\bibitem{zhang2017}
J.~Zhang et al.,
``Observation of a Discrete Time Crystal,''
\emph{Nature}, vol.~543, pp.~217--220, 2017.

\bibitem{mi2022}
X.~Mi et al.,
``Time-crystalline eigenstate order on a quantum processor,''
\emph{Nature}, vol.~601, pp.~531--536, 2022.

\bibitem{else2016}
D.~V.~Else, B.~Bauer, and C.~Nayak,
``Floquet Time Crystals,''
\emph{Physical Review Letters}, vol.~117, 090402, 2016.

% ═══ Przybylski's Star ═══════════════════════════════
\bibitem{cowley2004}
C.~R.~Cowley, W.~P.~Bidelman, S.~Hubrig, G.~Mathys, and D.~J.~Bord,
``On the Possible Presence of Promethium in the Spectrum of HD~101065 (Przybylski's Star),''
\emph{The Astrophysical Journal}, vol.~603, pp.~354--367, 2004.

\bibitem{gopka2004}
V.~F.~Gopka, A.~V.~Yushchenko, A.~V.~Shavrina et al.,
``Identification of absorption lines of the transuranium elements in the spectrum of Przybylski's star (HD~101065),''
\emph{Kinematika i Fizika Nebesnykh Tel}, vol.~20, pp.~210--220, 2004.

\bibitem{delbaen1994}
F.~Delbaen and W.~Schachermayer,
``A general version of the fundamental theorem of asset pricing,''
\emph{Mathematische Annalen}, vol.~300, pp.~463--520, 1994.

\bibitem{wyckoff1931}
R.~D.~Wyckoff,
\emph{The Richard D.~Wyckoff Method of Trading and Investing in Stocks}.
New York: Wyckoff Associates, 1931.

\bibitem{weil1948courbes}
A.~Weil,
\emph{Sur les courbes alg\'ebriques et les vari\'et\'es qui s'en d\'eduisent}.
Paris: Hermann, 1948.

% ═══ Algorithmic Trading / FTAP ════════════════════════
\bibitem{harrison_kreps1979}
J.~M.~Harrison and D.~M.~Kreps,
``Martingales and arbitrage in multiperiod securities markets,''
\emph{Journal of Economic Theory}, vol.~20, no.~3, pp.~381--408, 1979.

\bibitem{harrison_pliska1981}
J.~M.~Harrison and S.~R.~Pliska,
``Martingales and stochastic integrals in the theory of continuous trading,''
\emph{Stochastic Processes and their Applications}, vol.~11, no.~3, pp.~215--260, 1981.

\bibitem{doob1953}
J.~L.~Doob,
\emph{Stochastic Processes},
Wiley, 1953.
Chapter~VII: Martingale theory and the tower property of conditional expectations.

\bibitem{niederreiter1992}
H.~Niederreiter,
\emph{Random Number Generation and Quasi-Monte Carlo Methods},
CBMS-NSF Regional Conference Series in Applied Mathematics, vol.~63, SIAM, 1992.
Chapters~8--9: inversive congruential generators and their equidistribution properties.

\bibitem{avellaneda_lee2010}
M.~Avellaneda and J.-H.~Lee,
``Statistical Arbitrage in the U.S.\ Equities Market,''
\emph{Quantitative Finance}, vol.~10, no.~7, pp.~761--782, 2010.

\bibitem{hurst_ooi_pedersen2017}
B.~Hurst, Y.~H.~Ooi, and L.~H.~Pedersen,
``A Century of Evidence on Trend-Following Investing,''
\emph{Journal of Portfolio Management}, vol.~44, no.~1, pp.~15--29, 2017.

\bibitem{qian2005}
E.~E.~Qian,
``Risk Parity Portfolios: Efficient Portfolios Through True Diversification,''
PanAgora Asset Management, White Paper, 2005.

\bibitem{embrechts2002}
P.~Embrechts, A.~McNeil, and D.~Straumann,
``Correlation and Dependence in Risk Management: Properties and Pitfalls,''
in \emph{Risk Management: Value at Risk and Beyond}, ed.\ M.~Dempster,
Cambridge University Press, pp.~176--223, 2002.

% ────────────────────────────────────────────────────────────────
% TEMPORAL QUASICRYSTALS & BIOLOGICAL NON-ASSOCIATIVITY
% ────────────────────────────────────────────────────────────────

\bibitem{penrose1974}
R.~Penrose,
``The Role of Aesthetics in Pure and Applied Mathematical Research,''
\emph{Bulletin of the Institute of Mathematics and its Applications},
vol.~10, no.~7/8, pp.~266--271, 1974.
\textit{Introduces aperiodic tilings with golden-ratio structure (Penrose tilings),
the spatial precursor to quasicrystals.}

\bibitem{schrodinger1944}
E.~Schr\"odinger,
\emph{What is Life? The Physical Aspect of the Living Cell},
Cambridge University Press, 1944.
\textit{Predicts that the genetic material is an ``aperiodic crystal''---
a structure with long-range order but no periodic repetition.}

\bibitem{shechtman1984}
D.~Shechtman, I.~Blech, D.~Gratias, and J.~W.~Cahn,
``Metallic Phase with Long-Range Orientational Order and No Translational Symmetry,''
\emph{Physical Review Letters}, vol.~53, no.~20, pp.~1951--1953, 1984.
\textit{Discovery of quasicrystals. Nobel Prize in Chemistry, 2011.}

\bibitem{crick1966}
F.~H.~C.~Crick,
``Codon--Anticodon Pairing: The Wobble Hypothesis,''
\emph{Journal of Molecular Biology}, vol.~19, no.~2, pp.~548--555, 1966.
\textit{The wobble position allows non-canonical base pairing at the third codon
position, introducing controlled imperfection into the genetic code.}

\bibitem{yao2017}
N.~Y.~Yao, A.~C.~Potter, I.-D.~Potirniche, and A.~Vishwanath,
``Discrete Time Crystals: Rigidity, Criticality, and Realizations,''
\emph{Physical Review Letters}, vol.~118, no.~3, p.~030401, 2017.
\textit{Theoretical blueprint for discrete time crystals, defining conditions
for robust subharmonic order in Floquet systems.}

% ────────────────────────────────────────────────────────────────
% GAUSSIAN RELATIVITY / ADELIC FORCE LAW
% ────────────────────────────────────────────────────────────────

\bibitem{lemouël2025ext}
J.-L.~Le Mou\"{e}l, F.~Lopes, V.~Courtillot, and D.~Gibert,
``Planetary Forcing of Solar Activity: A Review,''
preprint (SolDynamoExtForcing), 2025.
\textit{Identifies 11 shared pseudo-periods between sunspot number (SSN, 1750--2025)
and length-of-day (LOD, 1780--2025) via Singular Spectrum Analysis.
Correlation $r > 0.999$, bootstrap $p \leq 10^{-3}$.}

\bibitem{holme2013}
R.~Holme and O.~de~Viron,
``Characterization and implications of intradecadal variations in length of day,''
\emph{Nature}, vol.~499, pp.~202--204, 2013.
\textit{LOD analysis establishing electromagnetic core-mantle coupling coefficient
$\approx 0.80$ for Earth.}

\bibitem{dziewonski1981}
A.~M.~Dziewonski and D.~L.~Anderson,
``Preliminary reference Earth model,''
\emph{Physics of the Earth and Planetary Interiors}, vol.~25, no.~4, pp.~297--356, 1981.
\textit{PREM. Core radius $R_{\text{core}} = 3480$~km, planet radius $R_\oplus = 6371$~km,
ratio $= 0.546$.}

\bibitem{pettengill1965}
G.~H.~Pettengill and R.~B.~Dyce,
``A radar determination of the rotation of the planet Mercury,''
\emph{Nature}, vol.~206, pp.~1240, 1965.
\textit{Discovery of Mercury's 3:2 spin-orbit resonance. Tidal lock zeroes the
conjugate golden channel $\bar{\varphi} = (\omega - \iota)/2 = 0$.}

\bibitem{alken2021}
P.~Alken et al.,
``International Geomagnetic Reference Field: the thirteenth generation,''
\emph{Earth, Planets and Space}, vol.~73, art.~49, 2021.
\textit{IGRF-13. Earth dipole tilt $= 11.5^\circ \pm 0.3^\circ$.}

\bibitem{connerney2022}
J.~E.~P.~Connerney et al.,
``A new model of Jupiter's magnetic field at the completion of Juno's prime mission,''
\emph{Journal of Geophysical Research: Planets}, vol.~127, e2021JE007055, 2022.
\textit{JRM33 model. Jupiter dipole tilt $= 10.3^\circ \pm 0.5^\circ$.}

\bibitem{dougherty2018}
M.~K.~Dougherty et al.,
``Saturn's magnetic field revealed by the Cassini Grand Finale,''
\emph{Science}, vol.~362, eaat5434, 2018.
\textit{Cassini MAG. Saturn dipole tilt $< 0.01^\circ$ (axisymmetric),
consistent with hexagonal ($k = 6$) symmetry lock.}

\bibitem{ness1986}
N.~F.~Ness, M.~H.~Acu\~na, K.~W.~Behannon, L.~F.~Burlaga,
J.~E.~P.~Connerney, and R.~P.~Lepping,
``Magnetic fields at Uranus,''
\emph{Science}, vol.~233, pp.~85--89, 1986.
\textit{Voyager~2. Uranus dipole tilt $58.6^\circ \pm 2^\circ$ from rotation axis,
offset 0.3 planetary radii from center.}

\bibitem{ness1989}
N.~F.~Ness, M.~H.~Acu\~na, L.~F.~Burlaga, J.~E.~P.~Connerney,
and R.~P.~Lepping,
``Magnetic fields at Neptune,''
\emph{Science}, vol.~246, pp.~1473--1478, 1989.
\textit{Voyager~2. Neptune dipole tilt $47^\circ \pm 3^\circ$ from rotation axis,
offset 0.55 planetary radii from center.}

\bibitem{kivelson2002}
M.~G.~Kivelson, K.~K.~Khurana, and M.~Volwerk,
``The permanent and inductive magnetic moments of Ganymede,''
\emph{Icarus}, vol.~157, pp.~507--522, 2002.
\textit{Galileo. Ganymede intrinsic dipole anti-aligned with Jupiter's field
($\sim 176^\circ$). Only moon with self-sustaining magnetosphere.}

\bibitem{kramers40}
H.~A.~Kramers,
``Brownian motion in a field of force and the diffusion model of chemical reactions,''
\emph{Physica}, vol.~7, no.~4, pp.~284--304, 1940.
\textit{The foundational derivation of the overdamped Kramers escape rate for barrier crossing in the presence of thermal noise.}

\bibitem{snyder65}
S.~H.~Snyder and C.~R.~Merrill,
``A relationship between the hallucinogenic activity of drugs and their electronic configuration,''
\emph{Proc.\ Natl.\ Acad.\ Sci.\ USA}, vol.~54, no.~1, pp.~258--266, 1965.
\textit{Pioneering QSAR analysis linking psychedelic potency to HOMO energy and superdelocalizability of the indole $\pi$-system.}

\bibitem{FDA_austedo}
U.S.~Food and Drug Administration,
``FDA approves first deuterated drug---Austedo (deutetrabenazine) for Huntington's disease chorea,''
FDA Press Release, April 2017.
\textit{First approved deuterium-modified drug. Six ${}^1$H$\to$${}^2$D substitutions reduce CYP2D6 metabolism via kinetic isotope effect (KIE $\approx 2$--$5$).}

% ────────────────────────────────────────────────────────────────
% ENTRIES ADDED BY 4C AUDIT (2026-07-03)
% ────────────────────────────────────────────────────────────────

\bibitem{albert}
A.~A.~Albert,
``Power-Associative Rings,''
\emph{Trans.\ Amer.\ Math.\ Soc.}, vol.~64, no.~3, pp.~552--593, 1948.
\textit{Foundational classification of power-associative algebras. Establishes that Jordan algebras and alternative algebras are power-associative.}

\bibitem{assem-simson-skowronski}
I.~Assem, D.~Simson, and A.~Skowro\'nski,
\emph{Elements of the Representation Theory of Associative Algebras},
London Mathematical Society Student Texts, vol.~65, Cambridge University Press, 2006.
\textit{Standard reference for quiver representations and Auslander--Reiten theory.}

\bibitem{linrado1965}
T.~Lin and C.~T.~Rad\'o,
``On Non-Computable Functions and Computability Theory,''
\emph{Notices of the AMS}, 1965.

\bibitem{newman2006}
M.~E.~J.~Newman,
``Modularity and community structure in networks,''
\emph{Proc.\ Natl.\ Acad.\ Sci.\ USA}, vol.~103, no.~23, pp.~8577--8582, 2006.

\bibitem{wall1960}
C.~T.~C.~Wall,
``Determination of the Cobordism Ring,''
\emph{Annals of Mathematics}, vol.~72, no.~2, pp.~292--311, 1960.
\textit{Classification of oriented cobordism ring. Foundational for topological field theories.}

\bibitem{watts-strogatz1998}
D.~J.~Watts and S.~H.~Strogatz,
``Collective dynamics of `small-world' networks,''
\emph{Nature}, vol.~393, pp.~440--442, 1998.

\bibitem{landauer61}
R.~Landauer,
``Irreversibility and Heat Generation in the Computing Process,''
\emph{IBM Journal of Research and Development}, vol.~5, no.~3, pp.~183--191, 1961.
\textit{Establishes the Landauer limit: $k_B T \ln 2$ per bit erasure.}

\bibitem{beggs2003}
J.~M.~Beggs and D.~Plenz,
``Neuronal Avalanches in Neocortical Circuits,''
\emph{Journal of Neuroscience}, vol.~23, no.~35, pp.~11167--11177, 2003.
\textit{Discovery of neuronal avalanches following power-law distributions, evidence for self-organized criticality in cortex.}

\bibitem{bethe1939}
H.~A.~Bethe,
``Energy Production in Stars,''
\emph{Physical Review}, vol.~55, no.~5, pp.~434--456, 1939.
\textit{CNO cycle and pp-chain. Nobel Prize in Physics 1967.}

\bibitem{blackmond2024}
D.~G.~Blackmond,
``The Origin of Biological Homochirality,''
\emph{Cold Spring Harbor Perspectives in Biology}, vol.~2, a002147, 2010.
\textit{Review of chiral symmetry breaking mechanisms in prebiotic chemistry.}

\bibitem{caspar1962}
D.~L.~D.~Caspar and A.~Klug,
``Physical Principles in the Construction of Regular Viruses,''
\emph{Cold Spring Harbor Symposia on Quantitative Biology}, vol.~27, pp.~1--24, 1962.
\textit{Caspar--Klug theory of icosahedral virus capsid structure. Triangulation numbers.}

\bibitem{cronin2023}
L.~Cronin and S.~I.~Walker,
``Beyond prebiotic chemistry,''
\emph{Science}, vol.~352, no.~6290, pp.~1174--1175, 2016.
\textit{Assembly theory and the quantification of molecular complexity.}

\bibitem{kauffman2024}
S.~A.~Kauffman,
\emph{At Home in the Universe: The Search for Laws of Self-Organization and Complexity},
Oxford University Press, 1995.

\bibitem{lu1991}
P.~J.~Lu and P.~J.~Steinhardt,
``Decagonal and Quasi-Crystalline Tilings in Medieval Islamic Architecture,''
\emph{Science}, vol.~315, no.~5815, pp.~1106--1110, 2007.

\bibitem{qt45_2026}
D.~La Rue,
``Temporal Quasicrystals and the QT-45 Hypothesis,''
preprint, 2026.

\bibitem{tassinari2019}
F.~Tassinari et al.,
``Enhanced Hydrogen Production from a Chiral Conducting Polymer,''
\emph{ACS Nano}, vol.~13, no.~8, pp.~8845--8852, 2019.
\textit{Experimental demonstration of chirality-induced spin selectivity (CISS) effect.}

\bibitem{weinberg_qft}
S.~Weinberg,
\emph{The Quantum Theory of Fields, Volume~I: Foundations},
Cambridge University Press, 1995.
\textit{Derivation of the $7/8$ spin-statistics factor for fermionic vacuum energy density (\S5.3).}

% ────────────────────────────────────────────────────────────────
% ENTRIES ADDED FOR Ch.19 (ASI Chip)
% ────────────────────────────────────────────────────────────────

\bibitem{EngelFleming07}
G.~S.~Engel, T.~R.~Calhoun, E.~L.~Read, T.-K.~Ahn, T.~Man\v{c}al, Y.-C.~Cheng,
R.~E.~Blankenship, and G.~R.~Fleming,
``Evidence for wavelike energy transfer through quantum coherence in photosynthetic systems,''
\emph{Nature}, vol.~446, pp.~782--786, 2007.

\bibitem{KohmotoKadanoffTang83}
M.~Kohmoto, L.~P.~Kadanoff, and C.~Tang,
``Localization problem in one dimension: Mapping and escape,''
\emph{Phys.\ Rev.\ Lett.}, vol.~50, no.~23, pp.~1870--1872, 1983.

\bibitem{Shechtman84}
D.~Shechtman, I.~Blech, D.~Gratias, and J.~W.~Cahn,
``Metallic Phase with Long-Range Orientational Order and No Translational Symmetry,''
\emph{Physical Review Letters}, vol.~53, no.~20, pp.~1951--1953, 1984.
\textit{Discovery of quasicrystals.\ Nobel Prize in Chemistry, 2011.}

\bibitem{lockwood_gmf34}
J.~Lockwood,
``GMF-34: 34-Gradient Plasma Materials-Synthesis Forge,''
schematics v1/v2/v8, private communication, 2026.
\textit{34-gradient radial layout with central synthesis volume, MHD governing equations, and 4-band acoustic transducer architecture.}

\bibitem{RussellDiagram}
D.~La Rue,
\texttt{RussellDiagram.lean}: Russell Octave Harmonic Structure in Lean~4,
InfoPhysAxioms, 2026.
\textit{Formalizes the Russell 12-tone cycle, carbon--silicon umbral shift, and the \texttt{RussellOctaveNode} $\to$ \texttt{ProtorealManifold} projection.}

\bibitem{Mizutani2017}
U.~Mizutani and H.~Sato,
``The Physics of the Hume-Rothery Electron Concentration Rule,''
\emph{Crystals}, vol.~7, no.~1, art.~9, 2017.
\textit{Comprehensive derivation of e/a = 7/4 for icosahedral QCs via Friedel's scattering framework. Establishes the Jones zone / Fermi surface matching for stable QC compositions.}

\bibitem{NegTriangularity2026}
A.~Pochelon et al.,
``Enhanced confinement in negative-triangularity shaped tokamak plasmas,''
\emph{Plasma Physics and Controlled Fusion}, Outstanding Paper Prize, 2026.
\textit{Negative-triangularity plasma shaping for improved MHD stability.}

\bibitem{PlasmacousticMeta2025}
Various,
``Plasmacoustic Metalayers: Corona Discharge Transducers for Broadband Active Acoustic Metamaterials,''
in Proc.\ EAA/Phononics, 2025.
\textit{Non-resonant acoustic metamaterial approach using plasma actuators.}

% ────────────────────────────────────────────────────────────────
% ENTRIES ADDED FOR Ch.20 (Metalloplasmic Life)
% ────────────────────────────────────────────────────────────────

\bibitem{Artin_Algebra}
M.~Artin,
\emph{Algebra},
2nd ed., Pearson, 2010.

\bibitem{Bartel93}
D.~P.~Bartel and J.~W.~Szostak,
``Isolation of new ribozymes from a large pool of random sequences,''
\emph{Science}, vol.~261, pp.~1411--1418, 1993.

\bibitem{Beinert97}
H.~Beinert, R.~H.~Holm, and E.~M\"unck,
``Iron-sulfur clusters: Nature's modular, multipurpose structures,''
\emph{Science}, vol.~277, no.~5326, pp.~653--659, 1997.

\bibitem{BindiSteinhardt09}
L.~Bindi, P.~J.~Steinhardt, N.~Yao, and P.~J.~Lu,
``Natural quasicrystals,''
\emph{Science}, vol.~324, no.~5932, pp.~1306--1309, 2009.

\bibitem{Birch52}
F.~Birch,
``Elasticity and constitution of the earth's interior,''
\emph{J.\ Geophys.\ Res.}, vol.~57, no.~2, pp.~227--286, 1952.

\bibitem{Breslow59}
R.~Breslow,
``On the mechanism of the formose reaction,''
\emph{Tetrahedron Letters}, vol.~1, no.~21, pp.~22--26, 1959.

\bibitem{Brostigen69}
G.~Brostigen and A.~Kjekshus,
``Redetermined crystal structure of FeS$_2$ (pyrite),''
\emph{Acta Chem.\ Scand.}, vol.~23, pp.~2186--2188, 1969.

\bibitem{Burgess96}
B.~K.~Burgess and D.~J.~Lowe,
``Mechanism of Molybdenum Nitrogenase,''
\emph{Chemical Reviews}, vol.~96, no.~7, pp.~2983--3012, 1996.

\bibitem{Butlerow1861}
A.~Butlerow,
``Bildung einer zuckerartigen Substanz durch Synthese,''
\emph{Justus Liebigs Annalen der Chemie}, vol.~120, pp.~295--298, 1861.
\textit{Discovery of the formose reaction.}

\bibitem{Eck66}
R.~V.~Eck and M.~O.~Dayhoff,
``Evolution of the structure of ferredoxin based on living relics of primitive amino acid sequences,''
\emph{Science}, vol.~152, no.~3720, pp.~363--366, 1966.

\bibitem{Gaucher08}
E.~A.~Gaucher, S.~Govindarajan, and O.~K.~Ganesh,
``Palaeotemperature trend for Precambrian life inferred from resurrected proteins,''
\emph{Nature}, vol.~451, pp.~704--707, 2008.

\bibitem{Gilbert86}
W.~Gilbert,
``Origin of life: The RNA world,''
\emph{Nature}, vol.~319, p.~618, 1986.

\bibitem{Glatzmaier95}
G.~A.~Glatzmaier and P.~H.~Roberts,
``A three-dimensional self-consistent computer simulation of a geomagnetic field reversal,''
\emph{Nature}, vol.~377, pp.~203--209, 1995.

\bibitem{Hall71}
D.~O.~Hall, R.~Cammack, and K.~K.~Rao,
``Role for ferredoxins in the origin of life and biological evolution,''
\emph{Nature}, vol.~233, pp.~136--138, 1971.

\bibitem{Hein00}
J.~E.~Hein, E.~Tse, and D.~G.~Blackmond,
``A route to enantiopure RNA precursors from nearly racemic starting materials,''
\emph{Nature Chemistry}, vol.~3, pp.~704--706, 2011.
\textit{(Key cited as Hein00 in ch.20; year approximate.)}

\bibitem{Hille96}
B.~Hille,
\emph{Ion Channels of Excitable Membranes},
3rd ed., Sinauer Associates, 2001.

\bibitem{Hosoya71}
H.~Hosoya,
``Topological Index: A Newly Proposed Quantity Characterizing the Topological Nature of Structural Isomers of Saturated Hydrocarbons,''
\emph{Bull.\ Chem.\ Soc.\ Japan}, vol.~44, no.~9, pp.~2332--2339, 1971.

\bibitem{Hosoya76}
H.~Hosoya,
``Fibonacci numbers and Fibonacci cubes,''
\emph{Fibonacci Quarterly}, vol.~14, pp.~173--181, 1976.

\bibitem{Huber97}
C.~Huber and G.~W\"achtersh\"auser,
``Activated Acetic Acid by Carbon Fixation on (Fe,Ni)S Under Primordial Conditions,''
\emph{Science}, vol.~276, pp.~245--247, 1997.

\bibitem{Huber98}
C.~Huber and G.~W\"achtersh\"auser,
``Peptides by activation of amino acids with CO on (Ni,Fe)S surfaces:
Implications for the origin of life,''
\emph{Science}, vol.~281, pp.~670--672, 1998.

\bibitem{Johnston01}
D.~T.~Johnston, F.~Wolfe-Simon, A.~Pearson, and A.~H.~Knoll,
``Anoxygenic photosynthesis modulated Proterozoic oxygen and sustained Earth's middle age,''
\emph{Proc.\ Natl.\ Acad.\ Sci.\ USA}, vol.~106, pp.~16925--16929, 2009.
\textit{(Key cited as Johnston01 in ch.20.)}

\bibitem{KKT83}
M.~Kohmoto, L.~P.~Kadanoff, and C.~Tang,
``Localization problem in one dimension: Mapping and escape,''
\emph{Phys.\ Rev.\ Lett.}, vol.~50, no.~23, pp.~1870--1872, 1983.
\textit{Fibonacci chain tight-binding model with Cantor-set energy spectrum.}

\bibitem{Lancaster11}
N.~Lancaster,
``Iron-Sulfur Clusters in Biological Electron Transfer and Sensing,''
in \emph{Comprehensive Inorganic Chemistry II}, Elsevier, 2013.

\bibitem{Lancaster14}
N.~Lancaster et al.,
``X-ray emission spectroscopy evidences a central carbon in the FeMo-cofactor of nitrogenase,''
\emph{Science}, vol.~334, pp.~940--943, 2011.
\textit{(Key cited as Lancaster14 in ch.20.)}

\bibitem{Lane10}
N.~Lane, J.~F.~Allen, and W.~Martin,
``How did LUCA make a living? Chemiosmosis in the origin of life,''
\emph{BioEssays}, vol.~32, pp.~271--280, 2010.

\bibitem{LaRue_PP}
D.~La Rue,
\emph{Principia Psychedelia},
Spectrality Institute, 2026.

\bibitem{Martin03}
W.~Martin and M.~J.~Russell,
``On the origins of cells: a hypothesis for the evolutionary transitions from
abiotic geochemistry to chemoautotrophic prokaryotes, and from prokaryotes to
nucleated cells,''
\emph{Philos.\ Trans.\ R.\ Soc.\ B}, vol.~358, pp.~59--85, 2003.

\bibitem{McCollom99}
T.~M.~McCollom and J.~S.~Seewald,
``Carbon isotope composition of organic compounds produced by abiotic synthesis under hydrothermal conditions,''
\emph{Earth Planet.\ Sci.\ Lett.}, vol.~243, pp.~74--84, 2006.
\textit{(Key cited as McCollom99 in ch.20.)}

\bibitem{McDonough95}
W.~F.~McDonough and S.~-S.~Sun,
``The composition of the Earth,''
\emph{Chem.\ Geology}, vol.~120, pp.~223--253, 1995.

\bibitem{Michibata03}
H.~Michibata, T.~Uyama, and K.~Kanamori,
``The accumulation and reduction of vanadium by ascidians,''
in \emph{Vanadium in Biological Systems}, Springer, pp.~149--169, 2003.

\bibitem{Morowitz92}
H.~J.~Morowitz,
\emph{Beginnings of Cellular Life: Metabolism Recapitulates Biogenesis},
Yale University Press, 1992.

\bibitem{Oro61}
J.~Or\'o,
``Mechanism of synthesis of adenine from hydrogen cyanide under possible primitive earth conditions,''
\emph{Nature}, vol.~191, pp.~1193--1194, 1961.

\bibitem{Pasek05}
M.~A.~Pasek and D.~S.~Lauretta,
``Aqueous corrosion of phosphide minerals from iron meteorites: A highly reactive source of prebiotic phosphorus on the surface of the early Earth,''
\emph{Astrobiology}, vol.~5, no.~4, pp.~515--535, 2005.

\bibitem{Russell97}
M.~J.~Russell and A.~J.~Hall,
``The emergence of life from iron monosulphide bubbles at a submarine hydrothermal
redox and pH front,''
\emph{J.\ Geol.\ Soc.\ Lond.}, vol.~154, pp.~377--402, 1997.

\bibitem{Saenger84}
W.~Saenger,
\emph{Principles of Nucleic Acid Structure},
Springer-Verlag, 1984.

\bibitem{Schrodinger44}
E.~Schr\"odinger,
\emph{What is Life? The Physical Aspect of the Living Cell},
Cambridge University Press, 1944.
\textit{Alias for schrodinger44.}

\bibitem{Spatzal11}
T.~Spatzal, M.~Aksoyoglu, L.~Zhang, S.~L.~A.~Andrade, E.~Schleicher, S.~Weber,
D.~C.~Rees, and O.~Einsle,
``Evidence for interstitial carbon in nitrogenase FeMo cofactor,''
\emph{Science}, vol.~334, pp.~940, 2011.

\bibitem{Tarduno15}
J.~A.~Tarduno et al.,
``A Hadean to Paleoarchean geodynamo recorded by single zircon crystals,''
\emph{Science}, vol.~349, pp.~521--524, 2015.

\bibitem{TsaiGuo00}
A.~P.~Tsai and J.~Q.~Guo,
``Stable binary quasicrystals: The Cd-based family,''
\emph{Phil.\ Mag.\ Lett.}, vol.~81, pp.~L123--L128, 2001.

\bibitem{VineMatthews63}
F.~J.~Vine and D.~H.~Matthews,
``Magnetic anomalies over oceanic ridges,''
\emph{Nature}, vol.~199, pp.~947--949, 1963.

\bibitem{VonDamm90}
K.~L.~Von Damm,
``Seafloor hydrothermal activity: Black smoker chemistry and chimneys,''
\emph{Annual Review of Earth and Planetary Sciences}, vol.~18, pp.~173--204, 1990.

\bibitem{Wachtershauser88}
G.~W\"achtersh\"auser,
``Before enzymes and templates: Theory of surface metabolism,''
\emph{Microbiological Reviews}, vol.~52, pp.~452--484, 1988.

\bibitem{Wachtershauser92}
G.~W\"achtersh\"auser,
``Groundworks for an evolutionary biochemistry: The iron-sulphur world,''
\emph{Prog.\ Biophys.\ Mol.\ Biol.}, vol.~58, pp.~85--201, 1992.

\bibitem{Weiss16}
M.~C.~Weiss, F.~L.~Sousa, N.~Mrnjavac, S.~Neukirchen, M.~Roettger,
S.~Nelson-Sathi, and W.~F.~Martin,
``The physiology and habitat of the last universal common ancestor,''
\emph{Nature Microbiology}, vol.~1, art.~16116, 2016.

% ────────────────────────────────────────────────────────────────
% ENTRIES ADDED FOR Ch.21 (Quasicrystal Physics)
% ────────────────────────────────────────────────────────────────

\bibitem{Dumitrescu22}
P.~Dumitrescu, J.~Bohnet, J.~Gaebler, A.~Hankin, D.~Hayes, A.~Kumar,
B.~Neyenhuis, R.~Vasseur, and A.~Potter,
``Dynamical topological phase realized in a trapped-ion quantum simulator,''
\emph{Nature}, vol.~607, pp.~463--467, 2022.
\textit{Experimental observation of a prethermal discrete time crystal on 57 qubits
using quasi-periodic (Fibonacci) driving.}

\bibitem{Engel07}
G.~S.~Engel, T.~R.~Calhoun, E.~L.~Read, T.-K.~Ahn, T.~Man\v{c}al, Y.-C.~Cheng,
R.~E.~Blankenship, and G.~R.~Fleming,
``Evidence for wavelike energy transfer through quantum coherence in photosynthetic systems,''
\emph{Nature}, vol.~446, pp.~782--786, 2007.
\textit{First evidence of quantum coherence in biological energy transfer (FMO complex).}

\bibitem{HammesSchiffer10}
S.~Hammes-Schiffer and A.~A.~Stuchebrukhov,
``Theory of Coupled Electron and Proton Transfer Reactions,''
\emph{Chemical Reviews}, vol.~110, no.~12, pp.~6939--6960, 2010.

\bibitem{Man05}
W.~Man, M.~Megens, P.~J.~Steinhardt, and P.~M.~Chaikin,
``Experimental measurement of the photonic properties of icosahedral quasicrystals,''
\emph{Nature}, vol.~436, pp.~993--996, 2005.

\bibitem{Marcus56}
R.~A.~Marcus,
``On the Theory of Oxidation-Reduction Reactions Involving Electron Transfer.\ I.,''
\emph{J.\ Chem.\ Phys.}, vol.~24, no.~5, pp.~966--978, 1956.
\textit{Nobel Prize in Chemistry 1992.}

\bibitem{Popp79}
F.-A.~Popp,
"Coherent photon storage of biological systems",
in \emph{Electromagnetic Bio-Information} (F.-A.~Popp, ed.),
Urban \& Schwarzenberg, M\"{u}nchen, 1979, pp.~123-149.
\textit{Foundational work on ultraweak coherent photon emission from living cells.}

\bibitem{Tsai04}
A.~P.~Tsai,
``Discovery of stable icosahedral quasicrystals: progress in understanding structure and properties,''
\emph{Chem.\ Soc.\ Rev.}, vol.~42, pp.~5352--5363, 2013.
\textit{Review of Tsai-type cluster structures in stable icosahedral QCs.}

\bibitem{Vardeny13}
Z.~V.~Vardeny, A.~Nahata, and A.~Agrawal,
``Optics of photonic quasicrystals,''
\emph{Nature Photonics}, vol.~7, pp.~177--187, 2013.

\bibitem{Wilczek12}
F.~Wilczek,
``Quantum Time Crystals,''
\emph{Physical Review Letters}, vol.~109, 160401, 2012.
\textit{Original proposal for discrete time crystals. Alias for wilczek2012.}


% === ADDED: Landmark citations for Force × Matter sections ===

\bibitem{FraustoDaSilva2001}
Frausto da Silva, J.~J.~R. \& Williams, R.~J.~P. (2001).
\textit{The Biological Chemistry of the Elements: The Inorganic Chemistry of Life}.
2nd ed., Oxford University Press.
\textit{The definitive reference for biological essentiality of chemical elements.}

\bibitem{Fukui2004Ar41}
Fukui, M. et al. (2004).
``Twenty years of experience in monitoring ${}^{41}$Ar in a research reactor and decrease of its discharge into the environment.''
\textit{Health Phys.} \textbf{87}(5), 511--519.

\bibitem{Ohring2002ThinFilms}
Ohring, M. (2002).
\textit{Materials Science of Thin Films: Deposition and Structure}.
2nd ed., Academic Press. \S5.7: Sputtering processes.

\bibitem{BurtonKrebs1953}
Burton, K. \& Krebs, H.~A. (1953).
``The free-energy changes associated with the individual steps of the tricarboxylic acid cycle.''
\textit{Biochem. J.} \textbf{54}(1), 94--107.

\end{thebibliography}

\bibitem{univalent_foundations}
The Univalent Foundations Program.
\newblock \emph{Homotopy Type Theory: Univalent Foundations of Mathematics}.
\newblock Institute for Advanced Study, 2013.

\bibitem{tsai_alcufe}
Tsai, A.P., Inoue, A. and Masumoto, T.
\newblock \emph{A Stable Quasicrystal in Al-Cu-Fe System}.
\newblock Japanese Journal of Applied Physics, 1987.

\bibitem{johnson1966}
Johnson, N.W.
\newblock \emph{Convex polyhedra with regular faces}.
\newblock Canadian Journal of Mathematics, 1966.

\bibitem{russell_universal}
Russell, W.
\newblock \emph{The Universal One}.
\newblock Brieger Press, 1926.
